\chapter{RNA Base-Pairs and Base-Pair-Steps Dataset}
\label{appendix3a}
\bibliographystyle{nar}
\footnotesize{
\begin{landscape}
\begin{center}
\begin{longtable}{p{0.76cm}   p{0.74cm}  p{5.2cm}   p{5.2cm}  p{3.2cm}
    p{0.6cm} p{0.9cm} p{1.8cm}}
%This is the header for the first page of the table...=
\caption{RNA structures  with resolution  $<$ 3.5 \AA~ used in the  analysis of
base-pair interactions.}\\

\hline
ndb\_id      &     pdb\_id      &      \multicolumn{1}{c}{Title}     &
\multicolumn{1}{c}{First Author}  & \multicolumn{1}{c}{Journal} & Year
& \multicolumn{1}{c}{Volume} & \multicolumn{1}{c}{Pages} \\ \hline \hline
\endfirsthead

%This is the header for the remaining page(s) of the table...
\multicolumn{8}{r}{{\tablename} \thetable{} -- Continued} \\
\hline
ndb\_id      &     pdb\_id      &      \multicolumn{1}{c}{Title}     &
\multicolumn{1}{c}{First Author}  & \multicolumn{1}{c}{Journal} & Year
& \multicolumn{1}{c}{Volume} & \multicolumn{1}{c}{Pages} \\ \hline \hline
\endhead

\multicolumn{8}{r}{Continued on Next Page\ldots} \\
\endfoot
%This is the footer for the last page of the table...
\endlastfoot

ahib53 & 165d & Structure of a mispaired RNA double helix at 1.6-A resolution and implications for the prediction of RNA secondary structure. & W.B. Cruse, P. Saludjian, E. Biala, P. Strazewski, T. Prange, O. Kennard & Proc.Natl.Acad.Sci.USA & 1994 & 91 & 4160-4164 \\ \hline
ar0001 & 402d & Structure of an RNA internal loop consisting of tandem C-A+ base pairs. & S.B. Jang, L.W. Hung, Y.I. Chi, E.L. Holbrook, R.J. Carter, S.R. Holbrook & Biochemistry & 1998 & 37 & 11726-11731 \\ \hline
ar0002 & 405d & Structure of a 16-mer RNA duplex r(GCAGACUUAAAUCUGC)2 with wobble C.A+ mismatches. & B. Pan, S.N. Mitra, M. Sundaralingam & J.Mol.Biol. & 1998 & 283 & 977-984 \\ \hline
ar0003 & 406d & The 1.8 A crystal structure of a statically disordered 17 base-pair RNA duplex: principles of RNA crystal packing and its effect on nucleic acid structure. & S.A. Shah, A.T. Brunger & J.Mol.Biol. & 1999 & 285 & 1577-1588 \\ \hline
ar0004 & 409d & Crystal structure of an RNA octamer duplex r(CCCIUGGG)2 incorporating tandem I.U wobbles. & B. Pan, S.N. Mitra, L. Sun, D. Hart, M. Sundaralingam & Nucleic Acids Res. & 1998 & 26 & 5699-5706 \\ \hline
ar0006 & 420d & Crystal structure of an RNA 16-mer duplex R(GCAGAGUUAAAUCUGC)2 with nonadjacent G(syn).A+(anti) mispairs. & B. Pan, S.N. Mitra, M. Sundaralingam & Biochemistry & 1999 & 38 & 2826-2831 \\ \hline
ar0007 & 422d & Structure of the dodecamer r(GAUCACUUCGGU) with four 5\&apos;-overhang nucleotides. & S. Eswaramoorthy, S.T. Rao, B. Pan, M. Sundaralingam & Acta Crystallogr.,Sect.D & 2004 & 60 & 8-12 \\ \hline
ar0008 & 433d & Crystal structure of a 14 bp RNA duplex with non-symmetrical tandem GxU wobble base pairs. & J. Trikha, D.J. Filman, J.M. Hogle & Nucleic Acids Res. & 1999 & 27 & 1728-1739 \\ \hline
ar0009 & 434d & Crystal structure of acceptor stem of tRNA(Ala) from Escherichia coli shows unique G.U wobble base pair at 1.16 A resolution. & U. Mueller, H. Schubel, M. Sprinzl, U. Heinemann & RNA & 1999 & 5 & 670-677 \\ \hline
ar0010 & 435d & Crystal structure of acceptor stem of tRNA(Ala) from Escherichia coli shows unique G.U wobble base pair at 1.16 A resolution. & U. Mueller, H. Schubel, M. Sprinzl, U. Heinemann & RNA & 1999 & 5 & 670-677 \\ \hline
ar0011 & 438d & Crystal structure of an RNA duplex r(G GCGC CC)2 with non-adjacent G*U base pairs. & K. Shi, M. Wahl, M. Sundaralingam & Nucleic Acids Res. & 1999 & 27 & 2196-2201 \\ \hline
ar0012 & 439d & Structure of an RNA duplex with an unusual G.C pair in wobble-like conformation at 1.6 A resolution. & M. Perbandt, M. Vallazza, C. Lippmann, C. Betzel, V.A. Erdmann & Acta Crystallogr.,Sect.D & 2001 & 57 & 219-224 \\ \hline
ar0013 & 466d & Disorder and twin refinement of RNA heptamer double helices. & U. Mueller, Y.A. Muller, R. Herbst-Irmer, M. Sprinzl, U. Heinemann & Acta Crystallogr.,Sect.D & 1999 & 55 & 1405-1413 \\ \hline
ar0014 & 464d & Disorder and twin refinement of RNA heptamer double helices. & U. Mueller, Y.A. Muller, R. Herbst-Irmer, M. Sprinzl, U. Heinemann & Acta Crystallogr.,Sect.D & 1999 & 55 & 1405-1413 \\ \hline
ar0015 & 469d & Crystal structure and improved antisense properties of 2\&apos;-O-(2-methoxyethyl)-RNA. & M. Teplova, G. Minasov, V. Tereshko, G.B. Inamati, P.D. Cook, M. Manoharan, M. Egli & Nat.Struct.Biol. & 1999 & 6 & 535-539 \\ \hline
ar0016 & 468d & Crystal structure and improved antisense properties of 2\&apos;-O-(2-methoxyethyl)-RNA. & M. Teplova, G. Minasov, V. Tereshko, G.B. Inamati, P.D. Cook, M. Manoharan, M. Egli & Nat.Struct.Biol. & 1999 & 6 & 535-539 \\ \hline
ar0017 & 470d & Crystal structure and improved antisense properties of 2\&apos;-O-(2-methoxyethyl)-RNA. & M. Teplova, G. Minasov, V. Tereshko, G.B. Inamati, P.D. Cook, M. Manoharan, M. Egli & Nat.Struct.Biol. & 1999 & 6 & 535-539 \\ \hline
ar0018 & 471d & Crystal structure and improved antisense properties of 2\&apos;-O-(2-methoxyethyl)-RNA. & M. Teplova, G. Minasov, V. Tereshko, G.B. Inamati, P.D. Cook, M. Manoharan, M. Egli & Nat.Struct.Biol. & 1999 & 6 & 535-539 \\ \hline
ar0021 & 1qc0 & Crystal structures of two plasmid copy control related RNA duplexes: An 18 base pair duplex at 1.20 A resolution and a 19 base pair duplex at 1.55 A resolution. & P.S. Klosterman, S.A. Shah, T.A. Steitz & Biochemistry & 1999 & 38 & 14784-14792 \\ \hline
ar0022 & 472d & Synthesis and crystal structure of an octamer RNA r(guguuuac)/r(guaggcac) with G.G/U.U tandem wobble base pairs: comparison with other tandem G.U pairs. & J. Deng, M. Sundaralingam & Nucleic Acids Res. & 2000 & 28 & 4376-4381 \\ \hline
ar0023 & 1csl & The structure of the HIV-1 RRE high affinity rev binding site at 1.6 A resolution. & J.A. Ippolito, T.A. Steitz & J.Mol.Biol. & 2000 & 295 & 711-717 \\ \hline
ar0024 & 1d4r & The 2 A structure of helix 6 of the human signal recognition particle RNA & K. Wild, O. Weichenrieder, G.A. Leonard, S. Cusack & Structure Fold.Des. & 1999 & 7 & 1345-1352 \\ \hline
ar0025 & 1qbp & Crystal structure of a brominated RNA helix with four mismatched base pairs: An investigation into RNA conformational variability. & A.C. Anderson, R.H. O'Neil, D.J. Filman, C.A. Frederick & Biochemistry & 1999 & 38 & 12577-12585 \\ \hline
ar0026 & 1dqf & Two crystal forms of helix II of Xenopus laevis 5S rRNA with a cytosine bulge. & Y. Xiong, M. Sundaralingam & RNA & 2000 & 6 & 1316-1324 \\ \hline
ar0027 & 1dqh & Two crystal forms of helix II of Xenopus laevis 5S rRNA with a cytosine bulge. & Y. Xiong, M. Sundaralingam & RNA & 2000 & 6 & 1316-1324 \\ \hline
ar0028 & 1duq & The crystal structure of the Rev binding element of HIV-1 reveals novel base pairing and conformational variability. & L.W. Hung, E.L. Holbrook, S.R. Holbrook & Proc.Natl.Acad.Sci.USA & 2000 & 97 & 5107-5112 \\ \hline
ar0029 & 1fuf & Crystal structures of two forms of a 14-mer RNA/DNA chimer duplex with double UU bulges: a novel intramolecular U*(A x U) base triple. & J. Deng, Y. Xiong, C. Sudarsanakumar, K. Shi, M. Sundaralingam & RNA & 2001 & 7 & 1425-1431 \\ \hline
ar0031 & 1i7j & The 1.19 A X-ray structure of 2\&apos;-O-Me(CGCGCG)(2) duplex shows dehydrated RNA with 2-methyl-2,4-pentanediol in the minor groove. & D.A. Adamiak, W.R. Rypniewski, J. Milecki, R.W. Adamiak & Nucleic Acids Res. & 2001 & 29 & 4144-4153 \\ \hline
ar0032 & 1i9x & Crystal structure of a model branchpoint-U2 snRNA duplex containing bulged adenosines. & J.A. Berglund, M. Rosbash, S.C. Schultz & RNA & 2001 & 7 & 682-691 \\ \hline
ar0033 & 1ik5 & Crystal structures of two forms of a 14-mer RNA/DNA chimer duplex with double UU bulges: a novel intramolecular U*(A x U) base triple. & J. Deng, Y. Xiong, C. Sudarsanakumar, K. Shi, M. Sundaralingam & RNA & 2001 & 7 & 1425-1431 \\ \hline
ar0034 & 1j9h & Crystal structure of an RNA duplex r(gugucgcac)(2) with uridine bulges. & Y. Xiong, J. Deng, C. Sudarsanakumar, M. Sundaralingam & J.Mol.Biol. & 2001 & 313 & 573-582 \\ \hline
ar0035 & 1jzv & Crystal Structure of a Bulged RNA from the SL2 Stem-loop of the HIV-1 psi-RNA & Y. Xiong, C. Sudarsanakumar, J. Deng, M. Pan, M. Sundaralingam & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
ar0036 & 1kd3 & Crystal structures of r(GGUCACAGCCC)2. & V. Kacer, S.A. Scaringe, J.N. Scarsdale, J.P. Rife & Acta Crystallogr.,Sect.D & 2003 & 59 & 423-432 \\ \hline
ar0037 & 1kd4 & Crystal structures of r(GGUCACAGCCC)2. & V. Kacer, S.A. Scaringe, J.N. Scarsdale, J.P. Rife & Acta Crystallogr.,Sect.D & 2003 & 59 & 423-432 \\ \hline
ar0038 & 1kd5 & Crystal structures of r(GGUCACAGCCC)2. & V. Kacer, S.A. Scaringe, J.N. Scarsdale, J.P. Rife & Acta Crystallogr.,Sect.D & 2003 & 59 & 423-432 \\ \hline
ar0041 & 1lnt & Structure of an RNA dodecamer containing a fragment from SRP domain IV of Escherichia coli. & J. Deng, Y. Xiong, B. Pan, M. Sundaralingam & Acta Crystallogr.,Sect.D & 2003 & 59 & 1004-1011 \\ \hline
ar0044 & 1nlc & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes. & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0046 & 1o3z & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes. & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0048 & 1sa9 & Structures of two RNA octamers containing tandem G.A base pairs. & S.B. Jang, K. Baeyens, M.S. Jeong, J. SantaLucia, D. Turner, S.R. Holbrook & Acta Crystallogr.,Sect.D & 2004 & 60 & 829-835 \\ \hline
ar0049 & 1saq & Structures of two RNA octamers containing tandem G.A base pairs. & S.B. Jang, K. Baeyens, M.S. Jeong, J. SantaLucia, D. Turner, S.R. Holbrook & Acta Crystallogr.,Sect.D & 2004 & 60 & 829-835 \\ \hline
ar0050 & 1y6t & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0051 & 1y73 & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0052 & 1y6s & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0053 & 1y90 & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0054 & 1y95 & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0055 & 1wvd & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0056 & 1y99 & The crystal structure of the dimerization initiation site of genomic HIV-1 RNA reveals an extended duplex with two adenine bulges & E. Ennifar, M. Yusupov, P. Walter, R. Marquet, B. Ehresmann, C. Ehresmann, P. Dumas & Structure Fold.Des. & 1999 & 7 & 1439-1449 \\ \hline
ar0058 & 1yy0 & Crystal structures, reactivity and inferred acylation transition States for 2\&apos;-amine substituted RNA. & C.M. Gherghe, J.M. Krahn, K.M. Weeks & J.Am.Chem.Soc. & 2005 & 127 & 13622-13628 \\ \hline
ar0059 & 1yzd & Crystal structures, reactivity and inferred acylation transition States for 2\&apos;-amine substituted RNA. & C.M. Gherghe, J.M. Krahn, K.M. Weeks & J.Am.Chem.Soc. & 2005 & 127 & 13622-13628 \\ \hline
ar0060 & 1z79 & Crystal structures, reactivity and inferred acylation transition States for 2\&apos;-amine substituted RNA. & C.M. Gherghe, J.M. Krahn, K.M. Weeks & J.Am.Chem.Soc. & 2005 & 127 & 13622-13628 \\ \hline
ar0061 & 1z7f & Crystal structures, reactivity and inferred acylation transition States for 2\&apos;-amine substituted RNA. & C.M. Gherghe, J.M. Krahn, K.M. Weeks & J.Am.Chem.Soc. & 2005 & 127 & 13622-13628 \\ \hline
ar0062 & 1zev & The structural basis of myotonic dystrophy from the crystal structure of CUG repeats. & B.H. Mooers, J.S. Logue, J.A. Berglund & Proc.Natl.Acad.Sci.Usa & 2005 & 102 & 16626-16631 \\ \hline
ar0063 & 2a0p & Syntheses of 4\&apos;-thioribonucleosides and thermodynamic stability and crystal structure of RNA oligomers with incorporated 4\&apos;-thiocytosine & P. Haeberli, I. Berger, P.S. Pallan, M. Egli & Nucleic Acids Res. & 2005 & 33 & 3965-3975 \\ \hline
ar0064 & 1zx7 & Molecular recognition of RNA by neomycin and a restricted neomycin derivative & F. Zhao, Q. Zhao, K.F. Blount, Q. Han, Y. Tor, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2005 & 44 & 5329-5334 \\ \hline
ar0065 & 2ao5 & Structure of an RNA duplex r(GGCGBrUGCGCU)2 with terminal and internal tandem G.U base pairs. & R. Utsunomiya, K. Suto, D. Balasundaresan, A. Fukamizu, P.K. Kumar, H. Mizuno & Acta Crystallogr.,Sect.D & 2006 & 62 & 331-338 \\ \hline
ar0066 & 2fqn & Two conformational states in the crystal structure of the Homo sapiens cytoplasmic ribosomal decoding A site. & J. Kondo, A. Urzhumtsev, E. Westhof & Nucleic Acids Res. & 2006 & 34 & 676-685 \\ \hline
ar0067 & 2g3s & The crystal structure at 1.5 angstroms resolution of an RNA octamer duplex containing tandem G.U basepairs & S.B. Jang, L.W. Hung, M.S. Jeong, E.L. Holbrook, X. Chen, D.H. Turner, S.R. Holbrook & Biophys.J. & 2006 & 90 & 4530-4537 \\ \hline
ar0068 & 2g92 & Gene silencing activity of siRNAs with a ribo-difluorotoluyl nucleotide. & J. Xia, A. Noronha, I. Toudjarska, F. Li, A. Akinc, R. Braich, M. Frank-Kamenetsky, K.G. Rajeev, M. Egli, M. Manoharan & Acs Chem.Biol. & 2006 & 1 & 176-183 \\ \hline
ar0069 & 2g91 & Crystal Structure of an RNA nonamer r(GGUGCGC)d(BrC)r(C) at 1.5 A resolution & K. Shi, B. Pan, M. Sundaralingam & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
ar0070 & 2h1m & Synthesis, Oxidation Behavior, Crystallization and Structure of 2\&apos;-Methylseleno Guanosine Containing RNAs. & H. Moroder, C. Kreutz, K. Lang, A. Serganov, R. Micura & J.Am.Chem.Soc. & 2006 & 128 & 9909-9918 \\ \hline
ar0071 & 2nok & Functional architecture of HCV IRES domain II stabilized by divalent metal ions in the crystal and in solution. & S.M. Dibrov, H. Johnston-Cox, Y.H. Weng, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2007 & 46 & 226-229 \\ \hline
ar0072 & 2oe6 & Apramycin recognition by the human ribosomal decoding site. & T. Hermann, V. Tereshko, E. Skripkin, D.J. Patel & Blood Cells Mol.Dis. & 2007 & 38 & 193-198 \\ \hline
ar0073 & 2o3y & Differential Selectivity of Natural and Synthetic Aminoglycosides towards the Eukaryotic and Prokaryotic Decoding A Sites. & J. Kondo, M. Hainrichson, I. Nudelman, D. Shallom-Shezifi, C.M. Barbieri, D.S. Pilch, E. Westhof, T. Baasov & Chembiochem & 2007 & 8 & 1700-1709 \\ \hline
ar0074 & 2oij & A crystallographic study of the binding of 13 metal ions to two related RNA duplexes. & E. Ennifar, P. Walter, P. Dumas & Nucleic Acids Res. & 2003 & 31 & 2671-2682 \\ \hline
ar0075 & 2oiy & Self-Cleaving Activity in the Duplex Form of the HIV-1(Lai) RNA Dimerization Initiation Site & E. Ennifar, P. Walter, P. Dumas & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
ar0076 & 2oj0 & Self-Cleaving Activity in the Duplex Form of the HIV-1(Lai) RNA Dimerization Initiation Site & E. Ennifar, P. Walter, P. Dumas & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
ar0080 & 2q1o & Crystal structure, stability and in vitro RNAi activity of oligoribonucleotides containing the ribo-difluorotoluyl nucleotide: insights into substrate requirements by the human RISC Ago2 enzyme. & F. Li, P.S. Pallan, M.A. Maier, K.G. Rajeev, S.L. Mathieu, C. Kreutz, Y. Fan, J. Sanghvi, R. Micura, E. Rozners, M. Manoharan, M. Egli & Nucleic Acids Res. & 2007 & 35 & 6424-6438 \\ \hline
ar0081 & 2r1s & The 1.3 A resolution structure of the RNA tridecamer r(GCGUUUGAAACGC): Metal ion binding correlates with base unstacking and groove contraction. & Y. Timsit, S. Bombard & RNA & 2007 & 13 & 2098-2107 \\ \hline
ar0082 & 2r20 & The 1.3 A resolution structure of the RNA tridecamer r(GCGUUUGAAACGC): Metal ion binding correlates with base unstacking and groove contraction. & Y. Timsit, S. Bombard & RNA & 2007 & 13 & 2098-2107 \\ \hline
ar0083 & 2r21 & 1.3 A resolution Structure of the tridecamer r(GCGUUUGAAACGC) & Y. Timsit, S. Bombard & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
ar0084 & 2r22 & The 1.3 A structure of the tridecamer r(GCGUUUGAAACGC) & Y. Timsit, S. Bombard & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
arf0108 & 377d & 1.76 A structure of a pyrimidine start alternating A-RNA hexamer r(CGUAC)dG. & R. Biswas, S.N. Mitra, M. Sundaralingam & Acta Crystallogr.,Sect.D & 1998 & 54 & 570-576 \\ \hline
arfs26 & 310d & Crystal structure of 2\&apos;-O-Me(CGCGCG)2, an RNA duplex at 1.30 A resolution. Hydration pattern of 2\&apos;-O-methylated RNA. & D.A. Adamiak, J. Milecki, M. Popenda, R.W. Adamiak, Z. Dauter, W.R. Rypniewski & Nucleic Acids Res. & 1997 & 25 & 4599-4607 \\ \hline
arh064 & 1rxb & The crystal structure of r(CCCCGGGG) in two distinct lattices. & S. Portmann, N. Usman, M. Egli & Biochemistry & 1995 & 34 & 7569-7575 \\ \hline
arh074 & 259d & RNA hydration: a detailed look. & M. Egli, S. Portmann, N. Usman & Biochemistry & 1996 & 35 & 8489-8494 \\ \hline
arl048 & 157d & Crystal and molecular structure of r(CGCGAAUUAGCG): an RNA duplex containing two G(anti).A(anti) base pairs. & G.A. Leonard, K.E. McAuley-Hecht, S. Ebel, D.M. Lough, T. Brown, W.N. Hunter & Structure & 1994 & 2 & 483-494 \\ \hline
arl062 & 1sdr & Crystal structure of an RNA dodecamer containing the Escherichia coli Shine-Dalgarno sequence. & H. Schindelin, M. Zhang, R. Bald, J.P. Furste, V.A. Erdmann, U. Heinemann & J.Mol.Biol. & 1995 & 249 & 595-603 \\ \hline
arn035 & 1rna & Crystallographic structure of an RNA helix: [U(UA)6A]2. & A.C. Dock-Bregeon, B. Chevrier, A. Podjarny, J. Johnson, J. S. Bear, G.R. Gough, P.T. Gilham, D. Moras & J.Mol.Biol. & 1989 & 209 & 459-474 \\ \hline
dr0001 & 418d & Crystal structure of an RNA duplex [r(gugcaca)dC]2 with 3\&apos;-dinucleoside overhangs forming a superhelix. & S.N. Mitra, R. Biswas, K. Shi, M. Sundaralingam & J.Biomol.Struct.Dyn. & 2000 & 11 & 189-194 \\ \hline
dr0004 & 1et4 & A water channel in the core of the vitamin B(12) RNA aptamer. & D. Sussman, C. Wilson & Structure Fold.Des. & 2000 & 8 & 719-727 \\ \hline
dr0005 & 1f27 & The 1.3 A crystal structure of a biotin-binding pseudoknot and the basis for RNA molecular recognition. & J. Nix, D. Sussman, C. Wilson & J.Mol.Biol. & 2000 & 296 & 1235-1244 \\ \hline
dr0006 & 1j7t & Crystal structure of paromomycin docked into the eubacterial ribosomal decoding A site. & Q. Vicens, E. Westhof & Structure & 2001 & 9 & 647-658 \\ \hline
dr0007 & 1lc4 & Crystal Structure of a Complex between the Aminoglycoside Tobramycin and an   & Q. Vicens, E. Westhof & Chem.Biol. & 2002 & 9 & 747-755 \\ \hline
dr0008 & 1mwl & Crystal structure of geneticin bound to a bacterial 16S ribosomal RNA A site oligonucleotide & Q. Vicens, E. Westhof & J.Mol.Biol. & 2003 & 326 & 1175-1188 \\ \hline
dr0009 & 1nta & Encapsulating Streptomycin within a small 40-mer RNA & V. Tereshko, E. Skripkin, D.J. Patel & chem.biol. & 2003 & 10 & 175-187 \\ \hline
dr0010 & 1ntb & Encapsulating Streptomycin within a small 40-mer RNA & V. Tereshko, E. Skripkin, D.J. Patel & chem.biol. & 2003 & 10 & 175-187 \\ \hline
dr0011 & 1yrj & Molecular recognition by glycoside pseudo base pairs and triples in an apramycin-RNA complex. & Q. Han, Q. Zhao, S. Fish, K.B. Simonsen, D. Vourloumis, J.M. Froelich, D. Wall, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2005 & 44 & 2694-2700 \\ \hline
dr0012 & 1o9m & The complex of a designer antibiotic with a model aminoacyl site of the 30S ribosomal subunit revealed by X-ray crystallography. & R.J. Russell, J.B. Murray, G. Lentzen, J. Haddad, S. Mobashery & J.Am.Chem.Soc. & 2003 & 125 & 3410-3411 \\ \hline
dr0013 & 1zz5 & Molecular recognition of RNA by neomycin and a restricted neomycin derivative & F. Zhao, Q. Zhao, K.F. Blount, Q. Han, Y. Tor, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2005 & 44 & 5329-5334 \\ \hline
dr0014 & 2a04 & Molecular recognition of RNA by neomycin and a restricted neomycin derivative & F. Zhao, Q. Zhao, K.F. Blount, Q. Han, Y. Tor, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2005 & 44 & 5329-5334 \\ \hline
dr0015 & 2et3 & Crystal structures of complexes between aminoglycosides and decoding A site oligonucleotides: role of the number of rings and positive charges in the specific binding leading to miscoding. & B. Francois, R.J. Russell, J.B. Murray, F. Aboul-ela, B. Masquida, Q. Vicens, E. Westhof & Nucleic Acids Res. & 2005 & 33 & 5677-5690 \\ \hline
dr0016 & 2et4 & Crystal structures of complexes between aminoglycosides and decoding A site oligonucleotides: role of the number of rings and positive charges in the specific binding leading to miscoding. & B. Francois, R.J. Russell, J.B. Murray, F. Aboul-ela, B. Masquida, Q. Vicens, E. Westhof & Nucleic Acids Res. & 2005 & 33 & 5677-5690 \\ \hline
dr0017 & 2et5 & Crystal structures of complexes between aminoglycosides and decoding A site oligonucleotides: role of the number of rings and positive charges in the specific binding leading to miscoding. & B. Francois, R.J. Russell, J.B. Murray, F. Aboul-ela, B. Masquida, Q. Vicens, E. Westhof & Nucleic Acids Res. & 2005 & 33 & 5677-5690 \\ \hline
dr0018 & 2et8 & Crystal structures of complexes between aminoglycosides and decoding A site oligonucleotides: role of the number of rings and positive charges in the specific binding leading to miscoding. & B. Francois, R.J. Russell, J.B. Murray, F. Aboul-ela, B. Masquida, Q. Vicens, E. Westhof & Nucleic Acids Res. & 2005 & 33 & 5677-5690 \\ \hline
dr0019 & 2be0 & Antibacterial aminoglycosides with a modified mode of binding to the ribosomal-RNA decoding site & B. Francois, J. Szychowski, S.S. Adhikari, K. Pachamuthu, E.E. Swayze, R.H. Griffey, M.T. Migawa, E. Westhof, S. Hanessian &Angew.Chem.Int.Ed. & 2004 & 43 & 6735-6738 \\ \hline
dr0020 & 2bee & Antibacterial aminoglycosides with a modified mode of binding to the ribosomal-RNA decoding site & B. Francois, J. Szychowski, S.S. Adhikari, K. Pachamuthu, E.E. Swayze, R.H. Griffey, M.T. Migawa, E. Westhof, S. Hanessian &Angew.Chem.Int.Ed. & 2004 & 43 & 6735-6738 \\ \hline
dr0021 & 2esi & Crystal structures of complexes between aminoglycosides and decoding A site oligonucleotides: role of the number of rings and positive charges in the specific binding leading to miscoding & B. Francois, R.J.M. Russel, J.B. Murray, F. Aboul-ela, B. Masquida, Q. Vicens, E. Westhof & Nucleic Acids Res. & 2005 & 33 & 5677-5790 \\ \hline
dr0022 & 2esj & Crystal structures of complexes between aminoglycosides and decoding A site oligonucleotides: role of the number of rings and positive charges in the specific binding leading to miscoding & B. Francois, R.J.M. Russel, J.B. Murray, F. Aboul-ela, B. Masquida, Q. Vicens, E. Westhof & Nucleic Acids Res. & 2005 & 33 & 5677-5690 \\ \hline
dr0023 & 2fcx & Targeting the dimerization initiation site of HIV-1 RNA with aminoglycosides: from crystal to cell. & E. Ennifar, J.C. Paillart, A. Bodlenner, P. Walter, J.-M. Weibel, A.-M. Aubertin, P. Pale, P. Dumas, R. Marquet & Nucleic Acids Res. & 2006 & 34 & 2328-2339 \\ \hline
dr0024 & 2fcy & Targeting the dimerization initiation site of HIV-1 RNA with aminoglycosides: from crystal to cell. & E. Ennifar, J.C. Paillart, A. Bodlenner, P. Walter, J.-M. Weibel, A.-M. Aubertin, P. Pale, P. Dumas, R. Marquet & Nucleic Acids Res. & 2006 & 34 & 2328-2339 \\ \hline
dr0025 & 2fcz & Targeting the dimerization initiation site of HIV-1 RNA with aminoglycosides: from crystal to cell. & E. Ennifar, J.C. Paillart, A. Bodlenner, P. Walter, J.-M. Weibel, A.-M. Aubertin, P. Pale, P. Dumas, R. Marquet & Nucleic Acids Res. & 2006 & 34 & 2328-2339 \\ \hline
dr0026 & 2fd0 & Targeting the dimerization initiation site of HIV-1 RNA with aminoglycosides: from crystal to cell. & E. Ennifar, J.C. Paillart, A. Bodlenner, P. Walter, J.-M. Weibel, A.-M. Aubertin, P. Pale, P. Dumas, R. Marquet & Nucleic Acids Res. & 2006 & 34 & 2328-2339 \\ \hline
dr0027 & 2f4s & Interactions of designer antibiotics and the bacterial ribosomal aminoacyl-tRNA site & J.B. Murray, S.O. Meroueh, R.J. Russell, G. Lentzen, J. Haddad, S. Mobashery & Chem.Biol. & 2006 & 13 & 129-138 \\ \hline
dr0028 & 2f4t & Interactions of designer antibiotics and the bacterial ribosomal aminoacyl-tRNA site & J.B. Murray, S.O. Meroueh, R.J. Russell, G. Lentzen, J. Haddad, S. Mobashery & Chem.Biol. & 2006 & 13 & 129-138 \\ \hline
dr0029 & 2f4u & Interactions of designer antibiotics and the bacterial ribosomal aminoacyl-tRNA site & J.B. Murray, S.O. Meroueh, R.J. Russell, G. Lentzen, J. Haddad, S. Mobashery & Chem.Biol. & 2006 & 13 & 129-138 \\ \hline
dr0030 & 2g5k & Crystal Structure of the Homo sapiens Cytoplasmic Ribosomal Decoding Site Complexed with Apramycin & J. Kondo, B. Francois, A. Urzhumtsev, E. Westhof & Angew.Chem.Int.Ed.Engl. & 2006 & 45 & 3310-3314 \\ \hline
dr0031 & 2g5q & Crystal structure of the bacterial ribosomal decoding site complexed with amikacin containing the gamma-amino-alpha-hydroxybutyryl (haba) group. & J. Kondo, R.J.M. Russell, J.B. Murray, E. Westhof & Biochimie & 2006 & 88 & 1027-1031 \\ \hline
dr0033 & 2o44 & Chemical parameters influencing fine tuning in the binding of Macrolide antibiotics to the ribosomal tunnel & E. Pyetan, D. Baram, T. Auerbach-Nevo, A. Yonath & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
dr0035 & 2oe5 & Apramycin recognition by the human ribosomal decoding site. & T. Hermann, V. Tereshko, E. Skripkin, D.J. Patel & Blood Cells Mol.Dis. & 2007 & 38 & 193-198 \\ \hline
dr0036 & 2oe8 & Apramycin recognition by the human ribosomal decoding site. & T. Hermann, V. Tereshko, E. Skripkin, D.J. Patel & Blood Cells Mol.Dis. & 2007 & 38 & 193-198 \\ \hline
dr0037 & 2o3v & Differential Selectivity of Natural and Synthetic Aminoglycosides towards the Eukaryotic and Prokaryotic Decoding A Sites. & J. Kondo, M. Hainrichson, I. Nudelman, D. Shallom-Shezifi, C.M. Barbieri, D.S. Pilch, E. Westhof, T. Baasov & Chembiochem & 2007 & 8 & 1700-1709 \\ \hline
dr0038 & 2o3w & Differential Selectivity of Natural and Synthetic Aminoglycosides towards the Eukaryotic and Prokaryotic Decoding A Sites. & J. Kondo, M. Hainrichson, I. Nudelman, D. Shallom-Shezifi, C.M. Barbieri, D.S. Pilch, E. Westhof, T. Baasov & Chembiochem & 2007 & 8 & 1700-1709 \\ \hline
dr0039 & 2o3x & Differential Selectivity of Natural and Synthetic Aminoglycosides towards the Eukaryotic and Prokaryotic Decoding A Sites. & J. Kondo, M. Hainrichson, I. Nudelman, D. Shallom-Shezifi, C.M. Barbieri, D.S. Pilch, E. Westhof, T. Baasov & Chembiochem & 2007 & 8 & 1700-1709 \\ \hline
dr0040 & 2pwt & Crystal Structure of the Bacterial Ribosomal Decoding Site Complexed with a Synthetic Doubly Functionalized Paromomycin Derivative: a New Specific Binding Mode to an A-Minor Motif Enhances in vitro Antibacterial Activity & J. Kondo, K. Pachamuthu, B. Francois, J. Szychowski, S. Hanessian, E. Westhof & Chemmedchem & 2007 & 2 & 1631-1638 \\ \hline
pr0001 & 5msf & Crystal structures of a series of RNA aptamers complexed to the same protein target. & S. Rowsell, N.J. Stonehouse, M.A. Convery, C.J. Adams, A.D. Ellington, I. Hirao, D.S. Peabody, P.G. Stockley, S.E. Phillips, M.A. Convery, S. Rowsell, N.J. Stonehouse, A.D. Ellington, I. Hirao, J.B. Murray, D.S. Peabody, S.E. Phillips, P.G. Stockley, K. Valegard, J.B. Murray, N.J. Stonehouse, Den name="Van P.G. Stockley, L. Liljas, K. Valegard, J.B. Murray, P.G. Stockley, N.J. Stonehouse, L. Liljas, R. Golmohammadi, K. Valegard, K. Fridborg, L. Liljas & Nat.Struct.Biol. & 1998 & 5 & 970-975 \\ \hline
pr0002 & 7msf & Crystal structures of a series of RNA aptamers complexed to the same protein target. & S. Rowsell, N.J. Stonehouse, M.A. Convery, C.J. Adams, A.D. Ellington, I. Hirao, D.S. Peabody, P.G. Stockley, S.E. Phillips, M.A. Convery, S. Rowsell, N.J. Stonehouse, A.D. Ellington, I. Hirao, J.B. Murray, D.S. Peabody, S.E. Phillips, P.G. Stockley, K. Valegard, J.B. Murray, N.J. Stonehouse, Den name="Van P.G. Stockley, L. Liljas, K. Valegard, J.B. Murray, P.G. Stockley, N.J. Stonehouse, L. Liljas, R. Golmohammadi, K. Valegard, K. Fridborg, L. Liljas & Nat.Struct.Biol. & 1998 & 5 & 970-975 \\ \hline
pr0003 & 1zdk & Crystallographic studies of RNA hairpins in complexes with recombinant MS2 capsids: implications for binding requirements. & E. Grahn, N.J. Stonehouse, J.B. Murray, den name="van K. Valegard, K. Fridborg, P.G. Stockley, L. Liljas, K. Valegard, J.B. Murray, P.G. Stockley, N.J. Stonehouse, L. Liljas, R. Golmohammadi, K. Valegard, K. Fridborg, L. Liljas & RNA & 1999 & 5 & 131-138 \\ \hline
pr0004 & 1b23 & The crystal structure of Cys-tRNACys-EF-Tu-GDPNP reveals general and specific features in the ternary complex and in tRNA. & P. Nissen, S. Thirup, M. Kjeldgaard, J. Nyborg, P. Nissen, M. Kjeldgaard, S. Thirup, G. Polekhina, L. Reshetnikova, B.F.C. Clark, J. Nyborg & Structure Fold.Des. & 1999 & 7 & 143-156 \\ \hline
pr0005 & 1drz & Crystal structure of a hepatitis delta virus ribozyme. & A.R. Ferre-D\&apos;Amare, K. Zhou, J.A. Doudna & Nature & 1998 & 395 & 567-574 \\ \hline
pr0006 & 1qf6 & The structure of threonyl-tRNA synthetase-tRNA(Thr) complex enlightens its repressor activity and reveals an essential zinc ion in the active site & R. Sankaranarayanan, A.C. Dock-Bregeon, P. Romby, J. Caillet, M. Springer, B. Rees, C. Ehresmann, B. Ehresmann, D. Moras & Cell (Cambridge,Mass.) & 1999 & 97 & 371-381 \\ \hline
pr0010 & 1cx0 & Crystal structure of a hepatitis delta virus ribozyme. & A.R. Ferre-D\&apos;Amare, K. Zhou, J.A. Doudna & Nature & 1998 & 395 & 567-574 \\ \hline
pr0013 & 1qu3 & Insights into editing from an ile-tRNA synthetase structure with tRNAile and mupirocin. & L.F. Silvian, J. Wang, T.A. Steitz, J. Wang, L.F. Silvian, T.A. Steitz, J. Wang, L.F. Silvian, T.A. Steitz, J. Wang, L.F. Silvian, T.A. Steitz & Science & 1999 & 285 & 1074-1077 \\ \hline
pr0014 & 1qu2 & Insights into editing from an ile-tRNA synthetase structure with tRNAile and mupirocin. & L.F. Silvian, J. Wang, T.A. Steitz, J. Wang, L.F. Silvian, T.A. Steitz, J. Wang, L.F. Silvian, T.A. Steitz, J. Wang, L.F. Silvian, T.A. Steitz & Science & 1999 & 285 & 1074-1077 \\ \hline
pr0015 & 1qa6 & Crystal structure of a conserved ribosomal protein-RNA complex. & G.L. Conn, D.E. Draper, E.E. Lattman, A.G. Gittis & Science & 1999 & 284 & 1171-1174 \\ \hline
pr0018 & 1dfu & Structure of Escherichia coli ribosomal protein L25 complexed with a 5S rRNA fragment at 1.8-A resolution. & M. Lu, T.A. Steitz & Proc.Natl.Acad.Sci.USA & 2000 & 97 & 2023-2028 \\ \hline
pr0019 & 1c0a & Synthesis of aspartyl-tRNA(Asp) in Escherichia coli--a snapshot of the second step. & S. Eiler, A. Dock-Bregeon, L. Moulinier, J.C. Thierry, D. Moras & Embo J. & 1999 & 18 & 6532-6541 \\ \hline
pr0021 & 1dul & Crystal structure of the ribonucleoprotein core of the signal recognition particle. & R.T. Batey, R.P. Rambo, L. Lucast, B. Rha, J.A. Doudna & Science & 2000 & 287 & 7505-7513 \\ \hline
pr0022 & 1ec6 & Sequence-specific RNA binding by a Nova KH domain: implications for paraneoplastic disease and the fragile X syndrome. & H.A. Lewis, K. Musunuru, K.B. Jensen, C. Edo, H. Chen, R.B. Darnell, S.K. Burley & Cell & 2000 & 100 & 1232-1239 \\ \hline
pr0023 & 1efw & An intermediate step in the recognition of tRNA(Asp) by aspartyl-tRNA synthetase. & C. Briand, A. Poterszman, S. Eiler, G. Webster, J. Thierry, D. Moras & J.Mol.Biol. & 2000 & 299 & 323-332 \\ \hline
pr0024 & 1eiy & The crystal structure of phenylalanyl-tRNA synthetase from thermus thermophilus complexed with cognate tRNAPhe. & Y. Goldgur, L. Mosyak, L. Reshetnikova, V. Ankilova, O. Lavrik, S. Khodyreva, M. Safro & Structure & 1997 & 5 & 1051-1060 \\ \hline
pr0025 & 1euq & Influence of transfer RNA tertiary structure on aminoacylation efficiency by glutaminyl and cysteinyl-tRNA synthetases. & L.D. Sherlin, T.L. Bullock, K.J. Newberry, R.S. Lipman, Y.M. Hou, B. Beijer, B.S. Sproat, J.J. Perona & J.Mol.Biol. & 2000 & 299 & 59-68 \\ \hline
pr0026 & 1euy & Influence of transfer RNA tertiary structure on aminoacylation efficiency by glutaminyl and cysteinyl-tRNA synthetases. & L.D. Sherlin, T.L. Bullock, K.J. Newberry, R.S. Lipman, Y.M. Hou, B. Beijer, B.S. Sproat, J.J. Perona & J.Mol.Biol. & 2000 & 299 & 431-446 \\ \hline
pr0027 & 1exd & Tertiary core rearrangements in a tight binding transfer RNA aptamer. & T.L. Bullock, L.D. Sherlin, J.J. Perona & Nat.Struct.Biol. & 2000 & 7 & 431-446 \\ \hline
pr0029 & 1gax & Structural basis for double-sieve discrimination of L-valine from L-isoleucine and L-threonine by the complex of tRNA(Val) and valyl-tRNA synthetase. & S. Fukai, O. Nureki, S. Sekine, A. Shimada, J. Tao, D.G. Vassylyev, S. Yokoyama & Cell & 2000 & 103 & 497-504 \\ \hline
pr0030 & 1f7u & tRNA aminoacylation by arginyl-tRNA synthetase: induced conformations during substrates binding & B. Delagoutte, D. Moras, J. Cavarelli, B. Delagoutte, G. Keith, D. Moras, J. Cavarelli & Embo J. & 2000 & 19 & 793-803 \\ \hline
pr0031 & 1f7v & tRNA aminoacylation by arginyl-tRNA synthetase: induced conformations during substrates binding & B. Delagoutte, D. Moras, J. Cavarelli, B. Delagoutte, G. Keith, D. Moras, J. Cavarelli & Embo J. & 2000 & 19 & 5599-5610 \\ \hline
pr0032 & 1ffy & Insights into editing from an ile-tRNA synthetase structure with tRNAile and mupirocin. & L.F. Silvian, J. Wang, T.A. Steitz & Science & 1999 & 285 & 5599-5610 \\ \hline
pr0035 & 1g59 & Structural basis for anticodon recognition by discriminating glutamyl-tRNA synthetase. & S. Sekine, O. Nureki, A. Shimada, D.G. Vassylyev, S. Yokoyama & Nat.Struct.Biol. & 2001 & 8 & 1074-1077 \\ \hline
pr0037 & 1hq1 & Structural and energetic analysis of RNA recognition by a universally conserved protein from the signal recognition particle. & R.T. Batey, M.B. Sagar, J.A. Doudna & J.Mol.Biol. & 2001 & 307 & 203-206 \\ \hline
pr0041 & 1e8o & Structure and Assembly of the Alu Domain of the Mammalian Signal Recognition Particle & O. Weichenrieder, K. Wild, K. Strub, S. Cusack & Nature & 2000 & 408 & 229-246 \\ \hline
pr0047 & 1i6u & Detailed analysis of RNA-protein interactions within the ribosomal protein S8-rRNA complex from the archaeon Methanococcus jannaschii. & S. Tishchenko, A. Nikulin, N. Fomenkova, N. Nevskaya, O. Nikonov, P. Dumas, H. Moine, B. Ehresmann, C. Ehresmann, W. Piendl, V. Lamzin, M. Garber, S. Nikonov, N. Nevskaya, S. Tishchenko, A. Nikulin, S. al-Karadaghi, A. Liljas, B. Ehresmann, C. Ehresmann, M. Garber, S. Nikonov, K. Kalurachci, E.P. Nikonowicz & J.Mol.Biol. & 2001 & 311 & 167-173 \\ \hline
pr0049 & 1il2 & The structure of an AspRS-tRNA(Asp) complex reveals a tRNA-dependent control mechanism. & L. Moulinier, S. Eiler, G. Eriani, J. Gangloff, J.C. Thierry, K. Gabriel, W.H. McClain, D. Moras & Embo J. & 2001 & 20 & 311-324 \\ \hline
pr0051 & 1jbr & Crystal structures of restrictocin-inhibitor complexes with implications for RNA recognition and base flipping. & X. Yang, T. Gerczei, L.T. Glover, C.C. Correll & Nat.Struct.Biol. & 2001 & 8 & 5290-5301 \\ \hline
pr0052 & 1jbs & Crystal structures of restrictocin-inhibitor complexes with implications for RNA recognition and base flipping. & X. Yang, T. Gerczei, L.T. Glover, C.C. Correll & Nat.Struct.Biol. & 2001 & 8 & 968-973 \\ \hline
pr0053 & 1jbt & Crystal structures of restrictocin-inhibitor complexes with implications for RNA recognition and base flipping. & X. Yang, T. Gerczei, L.T. Glover, C.C. Correll & Nat.Struct.Biol. & 2001 & 8 & 968-973 \\ \hline
pr0054 & 1jid & Crystal structure of an early protein-RNA assembly complex of the signal recognition particle. & K. Wild, I. Sinning, S. Cusack, K. Wild, O. Weichenrieder, G. name="Leonard, S. Cusack & Science & 2001 & 294 & 968-973 \\ \hline
pr0055 & 1e7k & Crystal structure of the spliceosomal 15.5kD protein bound to a U4 snRNA fragment. & I. Vidovic, S. Nottrott, K. Hartmuth, R. Luhrmann, R. Ficner, S. Nottrott, K. Hartmuth, P. Fabrizio, H. Urlaub, I. Vidovic, R. Ficner, R. Luhrmann & Mol.Cell & 2000 & 6 & 598-601 \\ \hline
pr0056 & 1h4q & A succession of substrate induced conformational changes ensures the amino acid specificity of Thermus thermophilus prolyl-tRNA synthetase: comparison with histidyl-tRNA synthetase. & A. Yaremchuk, M. Tukalo, M. Grotli, S. Cusack, A. Yaremchuk, S. Cusack, M. Tukalo, A. Yaremchuk, S. Cusack, M. Tukalo, A. Yaremchuk, I. Krikliviy, S. Cusack, M. Tukalo, S. Cusack, A. Yaremchuk, I. Krikliviy, M. Tukalo & J.Mol.Biol. & 2001 & 309 & 1331-1342 \\ \hline
pr0057 & 1h4s & A succession of substrate induced conformational changes ensures the amino acid specificity of Thermus thermophilus prolyl-tRNA synthetase: comparison with histidyl-tRNA synthetase. & A. Yaremchuk, M. Tukalo, M. Grotli, S. Cusack, A. Yaremchuk, S. Cusack, M. Tukalo, A. Yaremchuk, S. Cusack, M. Tukalo, A. Yaremchuk, I. Krikliviy, S. Cusack, M. Tukalo, S. Cusack, A. Yaremchuk, I. Krikliviy, M. Tukalo & J.Mol.Biol. & 2001 & 309 & 989-1002 \\ \hline
pr0059 & 2fmt & Crystal structure of methionyl-tRNAfMet transformylase complexed with the initiator formyl-methionyl-tRNAfMet. & E. Schmitt, M. Panvert, S. Blanquet, Y. Mechulam & Embo J. & 1998 & 17 & 989-1002 \\ \hline
pr0060 & 1k8w & Cocrystal structure of a tRNA Psi55 pseudouridine synthase: nucleotide flipping by an RNA-modifying enzyme. & C. Hoang, A.R. Ferre-D\&apos;Amare & Cell & 2001 & 107 & 6819-6826 \\ \hline
pr0064 & 1kog & Structural basis of translational control by Escherichia coli threonyl tRNA synthetase. & A. Torres-Larios, A.C. Dock-Bregeon, P. Romby, B. Rees, R. Sankaranarayanan, J. Caillet, M. Springer, C. Ehresmann, B. Ehresmann, D. Moras & Nat.Struct.Biol. & 2002 & 9 & 929-939 \\ \hline
pr0067 & 1l9a & Crystal structure of SRP19 in complex with the S domain of SRP RNA and its implication for the assembly of the signal recognition particle. & C. Oubridge, A. Kuglstatter, L. Jovine, K. Nagai & Mol.Cell & 2002 & 9 & 343-347 \\ \hline
pr0069 & 1ivs & Mechanism of molecular interactions for tRNA(Val) recognition by valyl-tRNA synthetase & S. Fukai, O. Nureki, S.-I. Sekine, A. Shimada, D.G. Vassylyev, S. Yokoyama, S. Fukai, O. Nureki, S. Sekine, A. Shimada, J. Tao, D.G. Vassylyev, S. Yokoyama & RNA & 2003 & 9 & 1251-1261 \\ \hline
pr0073 & 1lng & Structure of the SRP19 RNA complex and implications for signal recognition particle assembly. & T. Hainzl, S. Huang, A.E. Sauer-Eriksson & Nature & 2002 & 417 & 100-111 \\ \hline
pr0074 & 1m5k & Transition state stabilization by a catalytic RNA & P.B. Rupert, A.P. Massey, S.T. Sigurdsson, A.R. Ferre-D\&apos;Amare, P.B. Rupert, A.R. Ferre-D\&apos;Amare & Science & 2002 & 298 & 767-771 \\ \hline
pr0075 & 1m5o & Transition state stabilization by a catalytic RNA & P.B. Rupert, A.P. Massey, S.T. Sigurdsson, A.R. Ferre-D\&apos;Amare, P.B. Rupert, A.R. Ferre-D\&apos;Amare & Science & 2002 & 298 & 1421-1424 \\ \hline
pr0076 & 1m5p & Transition state stabilization by a catalytic RNA & P.B. Rupert, A.P. Massey, S.T. Sigurdsson, A.R. Ferre-D\&apos;Amare, P.B. Rupert, A.R. Ferre-D\&apos;Amare & Science & 2002 & 298 & 1421-1424 \\ \hline
pr0077 & 1m5v & Transition state stabilization by a catalytic RNA & P.B. Rupert, A.P. Massey, S.T. Sigurdsson, A.R. Ferre-D\&apos;Amare, P.B. Rupert, A.R. Ferre-D\&apos;Amare & Science & 2002 & 298 & 1421-1424 \\ \hline
pr0082 & 1mfq & Induced structural changes of 7SL RNA during the assembly of human   & A. Kuglstatter, C. Oubridge, K. Nagai & Nat.Struct.Biol. & 2002 & 9 & 1421-1424 \\ \hline
pr0083 & 1mji & Detailed analysis of RNA-protein interactions within the bacterial ribosomal & A. Perederina, N. Nevskaya, O. Nikonov, A. Nikulin, P. Dumas, M. Yao, I. Tanaka, M. Garber, G. Gongadze, S. Nikonov & RNA & 2002 & 8 & 740-744 \\ \hline
pr0085 & 1mzp & Structure of the L1 protuberance in the ribosome. & A. Nikulin, I. Eliseikina, S. Tishchenko, N. Nevskaya, N. Davydova, O. Platonova, W. Piendl, M. Selmer, A. Liljas, D. Drygin, R. Zimmermann, M. Garber, S. Nikonov & Nat.Struct.Biol. & 2003 & 10 & 1548-1547 \\ \hline
pr0089 & 1n77 & ATP binding by glutamyl-tRNA synthetase is switched to the productive mode by tRNA binding & S. Sekine, O. Nureki, D.Y. Dubois, S. Bernier, R. Chenevert, J. Lapointe, D.G. Vassylyev, S. Yokoyama, S. Sekine, O. Nureki, A. Shimada, D.G. Vassylyev, S. Yokoyama, O. Nureki, D.G. Vassylyev, K. Katayanagi, T. Shimizu, S. Sekine, T. Kigawa, T. Miyazawa, S. Yokoyama, K. Morikawa & Embo J. & 2003 & 22 & 104-108 \\ \hline
pr0090 & 1n78 & ATP binding by glutamyl-tRNA synthetase is switched to the productive mode by tRNA binding & S. Sekine, O. Nureki, D.Y. Dubois, S. Bernier, R. Chenevert, J. Lapointe, D.G. Vassylyev, S. Yokoyama, S. Sekine, O. Nureki, A. Shimada, D.G. Vassylyev, S. Yokoyama, O. Nureki, D.G. Vassylyev, K. Katayanagi, T. Shimizu, S. Sekine, T. Kigawa, T. Miyazawa, S. Yokoyama, K. Morikawa & Embo J. & 2003 & 22 & 676-688 \\ \hline
pr0092 & 1j1u & Structural basis for orthogonal tRNA specificities of tyrosyl-tRNA synthetases for genetic code expansion & T. Kobayashi, O. Nureki, R. Ishitani, A. Yaremchuk, M. Tukalo, S. Cusack, K. Sakamoto, S. Yokoyama & NAT.STRUCT.BIOL. & 2003 & 10 & 676-688 \\ \hline
pr0093 & 1j2b & Alternative Tertiary Structure of tRNA for Recognition by a Posttranscriptional Modification Enzyme & R. Ishitani, O. Nureki, N. Nameki, N. Okada, S. Nishimura, S. Yokoyama & Cell (Cambridge,Mass.) & 2003 & 113 & 425-432 \\ \hline
pr0094 & 1ooa & Crystal structure of NF-kappaB (p50)2 complexed to a high-affinity RNA aptamer. & D.B. Huang, D. Vu, L.A. Cassiday, J.M. Zimmerman, III, name="Maher G. Ghosh & Proc.Natl.Acad.Sci.USA & 2003 & 100 & 383-394 \\ \hline
pr0095 & 1o0b & Amino Acid Discrimination by a class I aminoacyl-tRNA synthetase   & T.L. Bullock, N. Uter, T.A. Nissan, J.J. Perona & J.Mol.Biol. & 2003 & 328 & 9268-9273 \\ \hline
pr0096 & 1o0c & Amino Acid Discrimination by a class I aminoacyl-tRNA synthetase   & T.L. Bullock, N. Uter, T.A. Nissan, J.J. Perona & J.Mol.Biol. & 2003 & 328 & 395-408 \\ \hline
pr0098 & 1p6v & Crystal structure of the transfer-RNA domain of transfer-messenger RNA in complex with SmpB & S. Gutmann, P.W. Haebel, L. Metzinger, M. Sutter, B. Felden, N. Ban & Nature & 2003 & 424 & 395-408 \\ \hline
pr0101 & 1q2r & Chemical trapping and crystal structure of a catalytic tRNA guanine transglycosylase covalent intermediate & W. Xie, X. Liu, R.H. Huang & Nat.Struct.Biol. & 2003 & 10 & 699-703 \\ \hline
pr0102 & 1q2s & Chemical trapping and crystal structure of a catalytic tRNA guanine transglycosylase covalent intermediate & W. Xie, X. Liu, R.H. Huang & Nat.Struct.Biol. & 2003 & 10 & 781-788 \\ \hline
pr0105 & 1r3e & Crystal Structure of tRNA Pseudouridine Synthase TruB and Its RNA Complex: RNA Recognition Through a Combination of Rigid Docking and Induced Fit & H. Pan, S. Agarwalla, D.T. Moustakas, J. Finer-Moore, R.M. Stroud & Proc.Natl.Acad.Sci.USA & 2003 & 100 & 781-788 \\ \hline
pr0106 & 1r9f & Recognition of small interfering RNA by a viral suppressor of RNA & K. Ye, L. Malinina, D.J. Patel & Nature & 2003 & 426 & 12648-12653 \\ \hline
pr0107 & 1rc7 & Noncatalytic Assembly of Ribonuclease III with Double-Stranded RNA. & J. Blaszczyk, J. Gan, J.E. Tropea, D.L. Court, D.S. Waugh, X. Ji, J. Blaszczyk, J.E. Tropea, M. Bubunenko, K.M. Routzahn, D.S. Waugh, D.L. Court, X. Ji & Structure & 2004 & 12 & 874-878 \\ \hline
pr0108 & 1rlg & Molecular Basis of Box C/D RNA-Protein Interactions; Cocrystal Structure of Archaeal L7Ae and a Box C/D RNA. & T. Moore, Y. Zhang, M.O. Fenley, H. Li & STRUCTURE & 2004 & 12 & 457-466 \\ \hline
pr0109 & 1rpu & Size selective recognition of siRNA by an RNA silencing suppressor & J.M. Vargason, G. Szittya, J. Burgyan, T.M.T. Hall & Cell (Cambridge,Mass.) & 2003 & 115 & 807-818 \\ \hline
pr0111 & 1s03 & The structure of a ribosomal protein S8/spc operon mRNA complex. & H.J. Merianos, J. Wang, P.B. Moore & RNA & 2004 & 10 & 799-811 \\ \hline
pr0114 & 1vbx & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 954-964 \\ \hline
pr0115 & 1vby & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 201-205 \\ \hline
pr0116 & 1vbz & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 201-205 \\ \hline
pr0117 & 1vc0 & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 201-205 \\ \hline
pr0118 & 1sjf & A conformational switch controls hepatitis delta virus ribozyme catalysis. & A. Ke, K. Zhou, F. Ding, J.H. Cate, J.A. Doudna & Nature & 2004 & 429 & 201-205 \\ \hline
pr0119 & 1vc5 & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 201-205 \\ \hline
pr0120 & 1vc6 & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 201-205 \\ \hline
pr0121 & 1vc7 & A Conformational Switch controls hepatitis delta virus ribozyme catalysis & A. Ke, K. Zhou, F. Ding, J.H.D. Cate, J.A. Doudna & nature & 2004 & 429 & 201-205 \\ \hline
pr0122 & 1sj3 & A Conformational Switch controls hepatitis delta virus ribozyme  & A. Ke, K. Zhou, F. Ding, J.H. Cate, J.A. Doudna & Nature & 2004 & 429 & 201-205 \\ \hline
pr0123 & 1sj4 & A Conformational Switch controls hepatitis delta virus ribozyme & A. Ke, K. Zhou, F. Ding, J.H. Cate, J.A. Doudna & Nature & 2004 & 429 & 201-205 \\ \hline
pr0124 & 1vfg & Structural basis for template-independent RNA polymerization. & K. Tomita, S. Fukai, R. Ishitani, T. Ueda, N. Takeuchi, D.G. Vassylyev, O. Nureki & Nature & 2004 & 430 & 201-205 \\ \hline
pr0125 & 1t0k & Joint X-Ray and NMR Refinement of the Yeast L30e-mRNA Complex & J.A. Chao, J.R. Williamson & Structure & 2004 & 12 & 700-704 \\ \hline
pr0128 & 1tfw & Mechanism of transfer RNA maturation by CCA-adding enzyme without using an oligonucleotide template. & Y. Xiong, T.A. Steitz & Nature & 2004 & 430 & 1165-1176 \\ \hline
pr0129 & 1tfy & Mechanism of transfer RNA maturation by CCA-adding enzyme without using an oligonucleotide template. & Y. Xiong, T.A. Steitz & Nature & 2004 & 430 & 640-645 \\ \hline
pr0132 & 1u1y & The crystal structure of a high affinity RNA stem-loop complexed with the bacteriophage MS2 capsid: further challenges in the modeling of ligand-RNA interactions. & W.T. Horn, M.A. Convery, N.J. Stonehouse, C.J. Adams, L. Liljas, S.E. Phillips, P.G. Stockley & RNA & 2004 & 10 & 640-645 \\ \hline
pr0133 & 1u6b & Crystal Structure of a Self-Splicing Group I Intron with Both Exons. & P.L. Adams, M.R. Stahley, A.B. Kosek, J. Wang, S.A. Strobel, P.L. Adams, M.R. Stahely, M.L. Gill, C. Berman, A.B. Kosek, J. Wang, S.A. Strobel, S.A. Strobel, P.L. Adams, M.R. Stahley, J. Wang, T.R. Cech, A.J. Zaug, P.J. Grabowaski, B. Reinhold-Hurek, D.A. Shub & Nature & 2004 & 430 & 1776-1782 \\ \hline
pr0134 & 1wne & Structure of Foot-and-Mouth Disease Virus RNA-dependent RNA Polymerase and Its Complex with a Template-Primer RNA & C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer & J.Biol.Chem. & 2004 & 279 & 45-50 \\ \hline
pr0135 & 1u0b & Shape-selective RNA recognition by cysteinyl-tRNA synthetase & S. Hauenstein, C.M. Zhang, Y.M. Hou, J.J. Perona & Nat.Struct.Mol.Biol. & 2004 & 11 & 47212-47221 \\ \hline
pr0136 & 1u63 & Ribosomal protein L1 recognizes the same specific structural motif in its target sites on the autoregulatory mRNA and 23S rRNA. & N. Nevskaya, S. Tishchenko, A. Gabdoulkhakov, E. Nikonova, O. Nikonov, A. Nikulin, O. Platonova, M. Garber, S. Nikonov, W. Piendl & Nucleic Acids Res. & 2005 & 33 & 1134-1141 \\ \hline
pr0141 & 1xok & Cofolding organizes alfalfa mosaic virus RNA and coat protein for replication. & L.M. Guogas, D.J. Filman, J.M. Hogle, L. Gehrke & Science & 2004 & 306 & 478-485 \\ \hline
pr0143 & 1wsu & Structural basis for mRNA recognition by elongation factor SelB & S. Yoshizawa, L. Rasubala, T. Ose, D. Kohda, D. Fourmy, K. Maenaka & Nat.Struct.Mol.Biol. & 2005 & 12 & 2108-2111 \\ \hline
pr0144 & 1y39 & Coevolution of Protein and RNA Structures within a Highly Conserved Ribosomal Domain & M.S. Dunstan, D. Guhathakurta, D.E. Draper, G.L. Conn & Chem.Biol. & 2005 & 12 & 198-203 \\ \hline
pr0145 & 1wz2 & The crystal structure of Leucyl-tRNA synthetase and tRNA(leucine) complex & R. Fukunaga, S. Yokoyama & to be published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 201-206 \\ \hline
pr0146 & 1ytu & Structural basis for 5\&apos;-end-specific recognition of guide RNA by the A. fulgidus Piwi protein. & J.B. Ma, Y.R. Yuan, G. Meister, Y. Pei, T. Tuschl, D.J. Patel & Nature & 2005 & 434 &   \\ \hline
pr0147 & 1yyk & Intermediate states of ribonuclease III in complex with double-stranded RNA & J. Gan, J.E. Tropea, B.P. Austin, D.L. Court, D.S. Waugh, X. Ji & Structure & 2005 & 13 & 666-670 \\ \hline
pr0148 & 1yyo & Intermediate states of ribonuclease III in complex with double-stranded RNA & J. Gan, J.E. Tropea, B.P. Austin, D.L. Court, D.S. Waugh, X. Ji & Structure & 2005 & 13 & 1435-1442 \\ \hline
pr0149 & 1yyw & Intermediate states of ribonuclease III in complex with double-stranded RNA & J. Gan, J.E. Tropea, B.P. Austin, D.L. Court, D.S. Waugh, X. Ji & Structure & 2005 & 13 & 1435-1442 \\ \hline
pr0150 & 1yz9 & Intermediate states of ribonuclease III in complex with double-stranded RNA & J. Gan, J.E. Tropea, B.P. Austin, D.L. Court, D.S. Waugh, X. Ji & Structure & 2005 & 13 & 1435-1442 \\ \hline
pr0151 & 1yvp & Structural Insights into RNA Quality Control: The Ro Autoantigen Binds Misfolded RNAs via Its Central Cavity & A.J. Stein, G. Fuchs, C. Fu, S.L. Wolin, K.M. Reinisch & Cell (Cambridge,Mass.) & 2005 & 121 & 1435-1442 \\ \hline
pr0153 & 1zbh & Structural basis for 3\&apos;-end specific recognition of histone mRNA stem-loop by 3\&apos;-exonuclease, a human nuclease that also targets siRNA & Y. Cheng, D.J. Patel & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 529-539 \\ \hline
pr0154 & 1ze2 & Conformational change of pseudouridine 55  & K. Phannachet, R.H. Huang & Nucleic Acids Res. & 2004 & 32 &   \\ \hline
pr0155 & 1zjw & tRNA-dependent Aminoacyl-adenylate Hydrolysis by a Nonediting Class I Aminoacyl-tRNA Synthetase. & I. Gruic-Sovulj, N. Uter, T. Bullock, J.J. Perona & J.Biol.Chem. & 2005 & 280 & 1422-1429 \\ \hline
pr0157 & 1zho & New insights into the interaction of ribosomal protein L1 with RNA. & N. Nevskaya, S. Tishchenko, S. Volchkov, V. Kljashtorny, E. Nikonova, O. Nikonov, A. Nikulin, C. Kohrer, W. Piendl, R. Zimmermann, P. Stockley, M. Garber, S. Nikonov & J.Mol.Biol. & 2006 & 355 & 23978-23986 \\ \hline
pr0158 & 1h3e & Class I tyrosyl-tRNA synthetase has a class II mode of cognate tRNA recognition. & A. Yaremchuk, I. Kriklivyi, M. Tukalo, S. Cusack & Embo J. & 2002 & 21 & 747-759 \\ \hline
pr0159 & 1hc8 & A Compact RNA Tertiary Structure Contains a Buried Backbone-K+ Complex & G.L. Conn, A.G. Gittis, E.E. Lattman, V.K. Misra, D.E. Draper, G.L. Conn, D.E. Draper, E.E. Lattman, A.G. Gittis & J.Mol.Biol. & 2002 & 318 & 3829-3840 \\ \hline
pr0160 & 1zl3 & Precursor complex structure of pseudouridine synthase TruB suggests coupling of active site perturbations to an RNA-sequestering peripheral protein domain & C. Hoang, C.S. Hamilton, E.G. Mueller, A.R. Ferre-D\&apos;Amare & Protein Sci. & 2005 & 14 & 963-973 \\ \hline
pr0161 & 2csx & Crystal structure of Aquifex aeolicus methionyl-tRNA synthetase complexed with tRNA(Met) & K. Nakanishi, Y. Ogiso, T. Nakama, S. Fukai, O. Nureki & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 2201-2206 \\ \hline
pr0162 & 2ct8 & Crystal structure of Aquifex aeolicus methionyl-tRNA synthetase complexed with tRNA(Met) and methionyl-adenylate anologue & K. Nakanishi, Y. Ogiso, T. Nakama, S. Fukai, O. Nureki & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
pr0163 & 2cv0 & Structural bases of transfer RNA-dependent amino acid recognition and activation by glutamyl-tRNA synthetase & S. Sekine, M. Shichiri, S. Bernier, R. Chenevert, J. Lapointe, S. Yokoyama & Structure & 2006 & 14 &   \\ \hline
pr0164 & 2cv1 & Glutamyl-tRNA synthetase from Thermus thermophilus in complex with tRNA(Glu), ATP, and an analog of L-glutamate: a quaternary complex & S. Sekine, S. Yokoyama & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 1791-1799 \\ \hline
pr0165 & 2cv2 & Structural bases of transfer RNA-dependent amino acid recognition and activation by glutamyl-tRNA synthetase & S. Sekine, M. Shichiri, S. Bernier, R. Chenevert, J. Lapointe, S. Yokoyama & Structure & 2006 & 14 &   \\ \hline
pr0167 & 1zse & Structural Basis of RNA Binding Discrimination between Bacteriophages Qbeta and MS2 & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E.V. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 1791-1799 \\ \hline
pr0168 & 2czj & Crystal structure of the tRNA domain of tmRNA from Thermus thermophilus HB8 & Y. Bessho, R. Shibata, S. Sekine, K. Murayama, M. Shirouzu, S. Yokoyama & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 487-495 \\ \hline
pr0169 & 2ab4 & Dissecting the roles of a strictly conserved tyrosine in substrate recognition and catalysis by pseudouridine 55 synthase. & K. Phannachet, Y. Elias, R.H. Huang & Biochemistry & 2005 & 44 &   \\ \hline
pr0170 & 1zzn & Structural evidence for a two-metal-ion mechanism of group I intron splicing. & M.R. Stahley, S.A. Strobel, P.L. Adams, M.R. Stahley, A.B. Kosek, J. Wang, S.A. Strobel, P.L. Adams, M.R. Stahley, M.L. Gill, A.B. Kosek, J. Wang, S.A. Strobel, T.R. Cech, A.J. Zaug, P.J. Grabowaski, B. Reinhold-Hurek, D.A. Shub & Science & 2005 & 309 & 15488-15494 \\ \hline
pr0171 & 2ake & Structure of human tryptophanyl-tRNA synthetase in complex with tRNA(Trp) reveals the molecular basis of tRNA recognition and specificity & N. Shen, L. Guo, B. Yang, Y. Jin, J. Ding & Nucleic Acids Res. & 2006 & 34 & 1587-1590 \\ \hline
pr0172 & 2ann & Structural insights into RNA recognition versus dimerization by KH domains of the neuronal splicing factor Nova-1 & L. Malinina, M. Teplova, K. Musunuru, A. Teplov, J.C. Darnell, S.K. Burley, R.B. Darnell, D.J. Patel & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 3246-3258 \\ \hline
pr0173 & 2anr & Structural insights into RNA recognition versus dimerization by KH domains of the neuronal splicing factor Nova-1 & L. Malinina, M. Teplova, K. Musunuru, A. Teplov, J.C. Darnell, S.K. Burley, R.B. Darnell, D.J. Patel & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
pr0176 & 2azx & Two conformations of a crystalline human tRNA synthetase-tRNA complex: implications for protein synthesis. & X.L. Yang, F.J. Otero, K.L. Ewalt, J. Liu, M.A. Swairjo, C. Kohrer, U.L. RajBhandary, R.J. Skene, D.E. McRee, P. Schimmel & Embo J. & 2006 & 25 &   \\ \hline
pr0177 & 2b2d & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2 & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E.V. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 2919-2929 \\ \hline
pr0178 & 2b2e & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2 & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E.V. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 487-495 \\ \hline
pr0179 & 2b2g & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2 & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E.V. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 487-495 \\ \hline
pr0180 & 2b3j & Crystal structure of Staphylococcus aureus tRNA adenosine deaminase TadA in complex with RNA. & H.C. Losey, A.J. Ruthenburg, G.L. Verdine & Nat.Struct.Mol.Biol. & 2006 & 13 & 487-495 \\ \hline
pr0181 & 2az0 & Dual modes of RNA-silencing suppression by Flock House virus protein B2. & J.A. Chao, J.H. Lee, B.R. Chapados, E.W. Debler, A. Schneemann, J.R. Williamson & Nat.Struct.Mol.Biol. & 2005 & 12 & 153-159 \\ \hline
pr0182 & 2az2 & Dual modes of RNA-silencing suppression by Flock House virus protein B2. & J.A. Chao, J.H. Lee, B.R. Chapados, E.W. Debler, A. Schneemann, J.R. Williamson & Nat.Struct.Mol.Biol. & 2005 & 12 & 952-957 \\ \hline
pr0184 & 2d6f & Structural basis of RNA-dependent recruitment of glutamine to the genetic code & H. Oshikane, K. Sheppard, S. Fukai, Y. Nakamura, R. Ishitani, T. Numata, R.L. Sherrer, L. Feng, E. Schmitt, M. Panvert, S. Blanquet, Y. Mechulam, D. Soll, O. Nureki & Science & 2006 & 312 & 952-957 \\ \hline
pr0185 & 2ez6 & Structural Insight into the Mechanism of Double-Stranded RNA Processing by Ribonuclease III. & J. Gan, J.E. Tropea, B.P. Austin, D.L. Court, D.S. Waugh, X. Ji & Cell (Cambridge,Mass.) & 2006 & 124 & 1950-1954 \\ \hline
pr0186 & 2f8k & Sequence-specific recognition of RNA hairpins by the SAM domain of Vts1p. & T. Aviv, Z. Lin, G. Ben-Ari, C.A. Smibert, F. Sicheri & Nat.Struct.Mol.Biol. & 2006 & 13 & 355-366 \\ \hline
pr0188 & 2f8s & A Potential Protein-RNA Recognition Event along the RISC-Loading Pathway from the Structure of A. aeolicus Argonaute with Externally Bound siRNA. & Y.R. Yuan, Y. Pei, H.Y. Chen, T. Tuschl, D.J. Patel & Structure & 2006 & 14 & 168-176 \\ \hline
pr0189 & 2f8t & A Potential Protein-RNA Recognition Event along the RISC-Loading Pathway from the Structure of A. aeolicus Argonaute with Externally Bound siRNA. & Y.R. Yuan, Y. Pei, H.Y. Chen, T. Tuschl, D.J. Patel & Structure & 2006 & 14 & 1557-1565 \\ \hline
pr0190 & 2fk6 & Structure of the ubiquitous 3\&apos; processing enzyme RNase Z bound to transfer RNA. & de name="Li N. Mathy, O. Pellegrini, C. Condon, de name="Li O. Pellegrini, C. Condon & Nat.Struct.Mol.Biol. & 2006 & 13 & 1557-1565 \\ \hline
pr0192 & 2der & Snapshots of tRNA sulphuration via an adenylated intermediate & T. Numata, Y. Ikeuchi, S. Fukai, T. Suzuki, O. Nureki & Nature & 2006 & 442 & 376-377 \\ \hline
pr0193 & 2det & Snapshots of tRNA sulphuration via an adenylated intermediate & T. Numata, Y. Ikeuchi, S. Fukai, T. Suzuki, O. Nureki & Nature & 2006 & 442 & 419-424 \\ \hline
pr0194 & 2deu & Snapshots of tRNA sulphuration via an adenylated intermediate & T. Numata, Y. Ikeuchi, S. Fukai, T. Suzuki, O. Nureki & Nature & 2006 & 442 & 419-424 \\ \hline
pr0197 & 2gjw & RNA Recognition and Cleavage by an Splicing Endonuclease & S. Xue, K. Calvin, H. Li & Science & 2006 & 312 & 419-424 \\ \hline
pr0198 & 2dlc & Structural basis for recognition of cognate tRNA by tyrosyl-tRNA synthetase from three kingdoms & M. Tsunoda, Y. Kusakabe, N. Tanaka, S. Ohno, M. Nakamura, T. Senda, T. Moriguchi, N. Asai, M. Sekine, T. Yokogawa, K. Nishikawa, K.T. Nakamura & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 902-910 \\ \hline
pr0199 & 1ob2 & Kirromycin Defines a Specific Domain Arrangement of Elongation Factor EF-TU & R.C. Nielsen, O. Kristensen, M. Kjeldgaard, S. Thirup, P. Nissen & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
pr0201 & 2c4z & Structural basis of pyrimidine specificity in the MS2 RNA hairpin-coat-protein complex. & E. Grahn, T. Moss, C. Helgstrand, K. Fridborg, M. Sundaram, K. Tars, H. Lago, N.J. Stonehouse, D.R. Davis, P.G. Stockley, L. Liljas & RNA & 2001 & 7 &   \\ \hline
pr0202 & 2bu1 & Structural basis of pyrimidine specificity in the MS2 RNA hairpin-coat-protein complex. & E. Grahn, T. Moss, C. Helgstrand, K. Fridborg, M. Sundaram, K. Tars, H. Lago, N.J. Stonehouse, D.R. Davis, P.G. Stockley, L. Liljas & RNA & 2001 & 7 & 1616-1627 \\ \hline
pr0203 & 2c4q & Structural basis of pyrimidine specificity in the MS2 RNA hairpin-coat-protein complex. & E. Grahn, T. Moss, C. Helgstrand, K. Fridborg, M. Sundaram, K. Tars, H. Lago, N.J. Stonehouse, D.R. Davis, P.G. Stockley, L. Liljas & RNA & 2001 & 7 & 1616-1627 \\ \hline
pr0204 & 2c4y & Structural basis of pyrimidine specificity in the MS2 RNA hairpin-coat-protein complex. & E. Grahn, T. Moss, C. Helgstrand, K. Fridborg, M. Sundaram, K. Tars, H. Lago, N.J. Stonehouse, D.R. Davis, P.G. Stockley, L. Liljas & RNA & 2001 & 7 & 1616-1627 \\ \hline
pr0205 & 1un6 & Crystal structure of a zinc-finger-RNA complex reveals two modes of molecular recognition. & D. Lu, M.A. Searles, A. Klug, M.A. Searles, D. Lu, A. Klug & Nature & 2003 & 426 & 1616-1627 \\ \hline
pr0206 & 2bgg & Structural insights into mRNA recognition from a PIWI domain-siRNA guide complex. & J.S. Parker, S.M. Roe, D. Barford, J.S. Parker, S.M. Roe, D. Barford & Nature & 2005 & 434 & 96-100 \\ \hline
pr0209 & 2c51 & Structural basis of pyrimidine specificity in the MS2 RNA hairpin-coat-protein complex. & E. Grahn, T. Moss, C. Helgstrand, K. Fridborg, M. Sundaram, K. Tars, H. Lago, N.J. Stonehouse, D.R. Davis, P.G. Stockley, L. Liljas & RNA & 2001 & 7 & 663-666 \\ \hline
pr0210 & 2gxb & A Left-Handed RNA Double Helix Bound by the Zalpha Domain of the RNA-Editing Enzyme ADAR1. & D. Placido, B.A. Brown, K. Lowenhaupt, A. Rich, A. Athanasiadis & Structure & 2007 & 15 & 1616-1627 \\ \hline
pr0212 & 2dr2 & Structure of human tryptophanyl-tRNA synthetase in complex with tRNA(Trp) reveals the molecular basis of tRNA recognition and specificity & N. Shen, L. Guo, B. Yang, Y. Jin, J. Ding & Nucleic Acids Res. & 2006 & 34 & 395-404 \\ \hline
pr0213 & 2dr5 & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 3246-3258 \\ \hline
pr0214 & 2dr7 & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 956-960 \\ \hline
pr0215 & 2dr8 & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 956-960 \\ \hline
pr0216 & 2dr9 & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 956-960 \\ \hline
pr0217 & 2dra & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 956-960 \\ \hline
pr0218 & 2drb & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 956-960 \\ \hline
pr0219 & 2du3 & Structural insights into the O-phosphoserine-tRNACys intermediate of RNA-dependent cysteine biosynthesis in archaea & R. Fukunaga, S. Yokoyama & NAT.STRUCT.MOL.BIOL. & 2007 & \multicolumn{1}{l}{} & 956-960 \\ \hline
pr0220 & 2du4 & Structural insights into the O-phosphoserine-tRNACys intermediate of RNA-dependent cysteine biosynthesis in archaea & R. Fukunaga, S. Yokoyama & NAT.STRUCT.MOL.BIOL. & 2007 & \multicolumn{1}{l}{} &   \\ \hline
pr0221 & 2du5 & Structural insights into the O-phosphoserine-tRNACys intermediate of RNA-dependent cysteine biosynthesis in archaea & R. Fukunaga, S. Yokoyama & NAT.STRUCT.MOL.BIOL. & 2007 & \multicolumn{1}{l}{} &   \\ \hline
pr0222 & 2du6 & Structural insights into the O-phosphoserine-tRNACys intermediate of RNA-dependent cysteine biosynthesis in archaea & R. Fukunaga, S. Yokoyama & NAT.STRUCT.MOL.BIOL. & 2007 & \multicolumn{1}{l}{} &   \\ \hline
pr0224 & 2hvy & Crystal structure of an H/ACA box ribonucleoprotein particle & L. Li, K. Ye & Nature & 2006 & 443 &   \\ \hline
pr0225 & 2hw8 & Structure of the ribosomal protein L1-mRNA complex at 2.1 A resolution: common features of crystal packing of L1-RNA complexes. & S. Tishchenko, E. Nikonova, A. Nikulin, N. Nevskaya, S. Volchkov, W. Piendl, M. Garber, S. Nikonov & ACTA CRYSTALLOGR.,SECT.D & 2006 & 62 & 302-307 \\ \hline
pr0226 & 2dvi & Complete crystallographic analysis of the dynamics of CCA sequence addition & K. Tomita, R. Ishitani, S. Fukai, O. Nureki & Nature & 2006 & 443 & 1545-1554 \\ \hline
pr0228 & 2dxi & Structural bases of transfer RNA-dependent amino acid recognition and activation by glutamyl-tRNA synthetase & S. Sekine, M. Shichiri, S. Bernier, R. Chenevert, J. Lapointe, S. Yokoyama & Structure & 2006 & 14 & 956-960 \\ \hline
pr0229 & 2i82 & Crystal structure of pseudouridine synthase RluA: indirect sequence readout through protein-induced RNA structure & C. Hoang, J. Chen, C.A. Vizthum, J.M. Kandel, C.S. Hamilton, E.G. Mueller, A.R. Ferre-D\&apos;Amare & Mol.Cell & 2006 & 24 & 1791-1799 \\ \hline
pr0232 & 2i91 & Structural and biochemical basis for misfolded RNA recognition by the Ro autoantigen. & G. Fuchs, A.J. Stein, C. Fu, K.M. Reinisch, S.L. Wolin & Nat.Struct.Mol.Biol. & 2006 & 13 & 535-545 \\ \hline
pr0233 & 2iy5 & The crystal structure of the ternary complex of phenylalanyl-tRNA synthetase with tRNAPhe and a phenylalanyl-adenylate analogue reveals a conformational switch of the CCA end. & N. Moor, O. Kotik-Kogan, D. Tworowski, M. Sukhanova, M. Safro & Biochemistry & 2006 & 45 & 1002-1009 \\ \hline
pr0235 & 2ipy & Structure of dual function iron regulatory protein 1 complexed with ferritin IRE-RNA. & W.E. Walden, A.I. Selezneva, J. Dupuy, A. Volbeda, J.C. Fontecilla-Camps, E.C. Theil, K. Volz, A.I. Selezneva, G. Cavigiolio, E.C. Theil, W.E. Walden, K. Volz & Science & 2006 & 314 & 10572-10583 \\ \hline
pr0239 & 2nue & A stepwise model for double-stranded RNA processing by ribonuclease III. & J. Gan, G. Shaw, J.E. Tropea, D.S. Waugh, D.L. Court, X. Ji & Mol.Microbiol. & 2007 & 67 & 1903-1908 \\ \hline
pr0240 & 2nuf & A stepwise model for double-stranded RNA processing by ribonuclease III. & J. Gan, G. Shaw, J.E. Tropea, D.S. Waugh, D.L. Court, X. Ji & Mol.Microbiol. & 2007 & 67 & 143-154 \\ \hline
pr0241 & 2nug & A stepwise model for double-stranded RNA processing by ribonuclease III. & J. Gan, G. Shaw, J.E. Tropea, D.S. Waugh, D.L. Court, X. Ji & Mol.Microbiol. & 2007 & 67 & 143-154 \\ \hline
pr0242 & 2nqp & How U38, 39, and 40 of Many tRNAs Become the Targets for Pseudouridylation by TruA. & S. Hur, R.M. Stroud & Mol.Cell & 2007 & 26 & 143-154 \\ \hline
pr0245 & 2bny & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2. & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 189-203 \\ \hline
pr0246 & 2bq5 & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2. & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 487-495 \\ \hline
pr0247 & 2bs0 & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2. & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 487-495 \\ \hline
pr0248 & 2bs1 & Structural basis of RNA binding discrimination between bacteriophages Qbeta and MS2. & W.T. Horn, K. Tars, E. Grahn, C. Helgstrand, A.J. Baron, H. Lago, C.J. Adams, D.S. Peabody, S.E. Phillips, N.J. Stonehouse, L. Liljas, P.G. Stockley & Structure & 2006 & 14 & 487-495 \\ \hline
pr0249 & 2nz4 & Structural Investigation of the GlmS Ribozyme Bound to Its Catalytic Cofactor & J.C. Cochrane, S.V. Lipchock, S.A. Strobel & Chem.Biol. & 2007 & 14 & 487-495 \\ \hline
pr0250 & 1ob5 & Enacyloxin IIa pinpoints a binding pocket of elongation factor Tu for development of novel antibiotics. & A. Parmeggiani, I.M. Krab, T. Watanabe, R.C. Nielsen, C. Dahlberg, J. Nyborg, P. Nissen & J.Biol.Chem. & 2006 & 281 & 97-105 \\ \hline
pr0251 & 2bh2 & A unique RNA Fold in the RumA-RNA-cofactor ternary complex contributes to substrate selectivity and enzymatic function. & T.T. Lee, S. Agarwalla, R.M. Stroud, T.T. Lee, S. Agarwalla, R.M. Stroud & Cell & 2005 & 120 & 2893-2900 \\ \hline
pr0252 & 2bte & The crystal structure of leucyl-tRNA synthetase complexed with tRNALeu in the post-transfer-editing conformation. & M. Tukalo, A. Yaremchuk, R. Fukunaga, S. Yokoyama, S. Cusack & Nat.Struct.Mol.Biol. & 2005 & 12 & 599-611 \\ \hline
pr0254 & 2byt & The crystal structure of leucyl-tRNA synthetase complexed with tRNALeu in the post-transfer-editing conformation. & M. Tukalo, A. Yaremchuk, R. Fukunaga, S. Yokoyama, S. Cusack & Nat.Struct.Mol.Biol. & 2005 & 12 & 923-930 \\ \hline
pr0257 & 2iz8 & Investigating the structural basis of purine specificity in the structures of MS2 coat protein RNA translational operator hairpins. & C. Helgstrand, E. Grahn, T. Moss, N.J. Stonehouse, K. Tars, P.G. Stockley, L. Liljas & Nucleic Acids Res. & 2002 & 30 & 923-930 \\ \hline
pr0259 & 2izn & Investigating the structural basis of purine specificity in the structures of MS2 coat protein RNA translational operator hairpins. & C. Helgstrand, E. Grahn, T. Moss, N.J. Stonehouse, K. Tars, P.G. Stockley, L. Liljas & Nucleic Acids Res. & 2002 & 30 & 2678-2685 \\ \hline
pr0260 & 2oih & Structural roles of monovalent cations in the HDV ribozyme. & A. Ke, F. Ding, J.D. Batchelor, J.A. Doudna & Structure & 2007 & 15 & 2678-2685 \\ \hline
pr0261 & 2oj3 & Structural roles of monovalent cations in the HDV ribozyme. & A. Ke, F. Ding, J.D. Batchelor, J.A. Doudna & Structure & 2007 & 15 & 281-287 \\ \hline
pr0262 & 2e9r & Sequential structures provide insights into the fidelity of RNA replication & C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer, C. Ferrer-Orta, A. Arias, R. Agudo, R. Perez-Luque, R. Escarmis, E. Domingo, N. Verdaguer, C. Ferrer-Orta, A. Arias, C. Escarmis, N. Verdaguer, C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer, A. Arias, R. Agudo, C. Ferrer-Orta, R. Perez-Luque, A. Airaksinen, E. Brocchi, E. Domingo, N. Verdaguer, C. Escarmis & Proc.Natl.Acad.Sci.Usa & 2007 & 104 & 281-287 \\ \hline
pr0263 & 2e9t & Sequential structures provide insights into the fidelity of RNA replication & C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer, C. Ferrer-Orta, A. Arias, R. Agudo, R. Perez-Luque, R. Escarmis, E. Domingo, N. Verdaguer, C. Ferrer-Orta, A. Arias, C. Escarmis, N. Verdaguer, C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer, A. Arias, R. Agudo, C. Ferrer-Orta, R. Perez-Luque, A. Airaksinen, E. Brocchi, E. Domingo, N. Verdaguer, C. Escarmis & Proc.Natl.Acad.Sci.Usa & 2007 & 104 & 9463-9468 \\ \hline
pr0264 & 2e9z & Sequential structures provide insights into the fidelity of RNA replication & C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer & Proc.Natl.Acad.Sci.Usa & 2007 & 104 & 9463-9468 \\ \hline
pr0266 & 2ec0 & Sequential structures provide insights into the fidelity of RNA replication & C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer, C. Ferrer-Orta, A. Arias, R. Agudo, R. Perez-Luque, R. Escarmis, E. Domingo, N. Verdaguer, C. Ferrer-Orta, A. Arias, C. Escarmis, N. Verdaguer, C. Ferrer-Orta, A. Arias, R. Perez-Luque, C. Escarmis, E. Domingo, N. Verdaguer, A. Arias, R. Agudo, C. Ferrer-Orta, R. Perez-Luque, A. Airaksinen, E. Brocchi, E. Domingo, N. Verdaguer, C. Escarmis & Proc.Natl.Acad.Sci.Usa & 2007 & 104 & 9463-9468 \\ \hline
pr0267 & 2ozb & Structure-Sensitive Binding of Human Prp31 to a Composite RNA-Protein Platform in U4 snRNP & S. Liu, P. Li, O. Dybkov, S. Nottrott, K. Hartmuth, R. Luehrmann, T. Carlomagno, M.C. Wahl & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 9463-9468 \\ \hline
pr0272 & 2uwm & Structure Basis for Dynamical Interdomain Movement and RNA Recognition of the Selenocystein-Specific Elongation Factor Selb & T. Ose, N. Soler, L. Rasubala, K. Kuroki, D. Kohda, D. Fourmy, S. Yoshizawa, K. Maenaka & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} &   \\ \hline
pr0274 & 2pxb & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 &   \\ \hline
pr0275 & 2pxd & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0276 & 2pxe & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0277 & 2pxf & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0278 & 2pxk & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0279 & 2pxl & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0280 & 2pxp & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0281 & 2pxq & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0282 & 2pxt & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0283 & 2pxu & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0284 & 2pxv & A General Strategy to Solve the Phase Problem in RNA Crystallography. & A.Y. Keel, R.P. Rambo, R.T. Batey, J.S. Kieft & Structure & 2007 & 15 & 761-772 \\ \hline
pr0285 & 2pjp & Structural insight into a molecular switch in tandem winged-helix motifs from elongation factor SelB. & N. Soler, D. Fourmy, S. Yoshizawa, N. Soler, D. Fourmy, S. Yoshizawa & J.Mol.Biol. & 2007 & 370 & 761-772 \\ \hline
pr0294 & 2r8s & Synthetic antibodies for specific recognition and crystallization of structured RNA & J.D. Ye, V. Tereshko, J.K. Frederiksen, A. Koide, F.A. Fellouse, S.S. Sidhu, S. Koide, A.A. Kossiakoff, J.A. Piccirilli & Proc.Natl.Acad.Sci.Usa & 2008 & 105 & 728-741 \\ \hline
pr0296 & 2qux & Structural basis for the coevolution of a viral RNA-protein complex. & J.A. Chao, Y. Patskovsky, S.C. Almo, R.H. Singer & Nat.Struct.Mol.Biol. & 2008 & 15 & 82-87 \\ \hline
pr0306 & 2rd2 & A rationally engineered misacylating aminoacyl-tRNA synthetase & T.L. Bullock, A. Rodriguez-Hernandez, E. Franzen, J.J. Perona, L.D. Sherlin, T.L. Bullock, T.A. Nissan, J.J. Perona, F.J. Lariviere, O.C. Uhlenbeck, S.A. Scaringe & To be Published & \multicolumn{1}{l}{} & 7 & 103-105 \\ \hline
pr0307 & 2re8 & A Rationally Engineered Misacylating Aminoacyl-tRNA synthetase & T.L. Bullock, A. Rodriguez-Hernandez, E. Franzen, J.J. Perona, L.D. Sherlin, T.L. Bullock, T.A. Nissan, J.J. Perona, F.J. Lariviere, O.C. Uhlenbeck, S.A. Scaringe & To be Published & \multicolumn{1}{l}{} & 7 & 1671-1678 \\ \hline
pr0309 & 2rfk & Substrate RNA positioning in the archaeal H/ACA ribonucleoprotein complex. & B. Liang, S. Xue, R.M. Terns, M.P. Terns, H. Li & Nat.Struct.Mol.Biol. & 2007 & \multicolumn{1}{l}{} & 1671-1678 \\ \hline
pr0313 & 3bsn & Structural insights into mechanisms of catalysis and inhibition in norwalk virus polymerase. & D.F. Zamyatkin, F. Parra, J.M. Alonso, D.A. Harki, B.R. Peterson, P. Grochulski, K.K. Ng & J.Biol.Chem. & 2008 & 283 &   \\ \hline
pr0314 & 3bso & Structural insights into mechanisms of catalysis and inhibition in norwalk virus polymerase. & D.F. Zamyatkin, F. Parra, J.M. Alonso, D.A. Harki, B.R. Peterson, P. Grochulski, K.K. Ng & J.Biol.Chem. & 2008 & 283 & 7705-7712 \\ \hline
prv002 & 1urn & Crystal structure at 1.92 A resolution of the RNA-binding domain of the U1A spliceosomal protein complexed with an RNA hairpin. & C. Oubridge, N. Ito, P.R. Evans, C.H. Teo, K. Nagai & Nature & 1994 & 372 & 7705-7712 \\ \hline
prv006 & 1zdi & The three-dimensional structures of two complexes between recombinant MS2 capsids and RNA operator fragments reveal sequence-specific protein-RNA interactions. & K. Valegard, J.B. Murray, N.J. Stonehouse, den name="van P.G. Stockley, L. Liljas, K. Valegard, J.B. Murray, P.G. Stockley, N.J. Stonehouse, L. Liljas, R. Golmohammadi, K. Valegard, K. Fridborg, L. Liljas & J.Mol.Biol. & 1997 & 270 & 432-438 \\ \hline
prv008 & 1aq3 & Crystal structures of MS2 coat protein mutants in complex with wild-type RNA operator fragments. & den name="van N.J. Stonehouse, K. Valegard, J.B. Murray, C. Walton, K. Fridborg, P.G. Stockley, L. Liljas & Nucleic Acids Res. & 1998 & 26 & 724-738 \\ \hline
prv009 & 1aq4 & Crystal structures of MS2 coat protein mutants in complex with wild-type RNA operator fragments. & den name="van N.J. Stonehouse, K. Valegard, J.B. Murray, C. Walton, K. Fridborg, P.G. Stockley, L. Liljas & Nucleic Acids Res. & 1998 & 26 & 1345-1351 \\ \hline
prv010 & 6msf & Crystal structure of an RNA aptamer-protein complex at 2.8 A resolution. & M.A. Convery, S. Rowsell, N.J. Stonehouse, A.D. Ellington, I. Hirao, J.B. Murray, D.S. Peabody, S.E. Phillips, P.G. Stockley, K. Valegard, J.B. Murray, N.J. Stonehouse, Den name="Van P.G. Stockley, L. Liljas, K. Valegard, J.B. Murray, P.G. Stockley, N.J. Stonehouse, L. Liljas, R. Golmohammadi, K. Valegard, K. Fridborg, L. Liljas & Nat.Struct.Biol. & 1998 & 5 & 1345-1351 \\ \hline
prv020 & 1a34 & Refined structure of satellite tobacco mosaic virus at 1.8 A resolution. & S.B. Larson, J. Day, A. Greenwood, A. McPherson, S.B. Larson, S. Koszelak, J. Day, A. Greenwood, J.A. Dodds, A. McPherson, S.B. Larson, S. Koszelak, J. Day, A. Greenwood, J.A. Dodds, A. McPherson, J. Day, A. McPherson, S. Koszelak, J.A. Dodds, A. McPherson & J.Mol.Biol. & 1998 & 277 & 133-139 \\ \hline
pte003 & 1qtq & How glutaminyl-tRNA synthetase selects glutamine. & V.L. Rath, L.F. Silvian, B. Beijer, B.S. Sproat, T.A. Steitz & Structure & 1998 & 6 & 37-59 \\ \hline
ptr002 & 1gts & Structural basis for transfer RNA aminoacylation by Escherichia coli glutaminyl-tRNA synthetase. & J.J. Perona, M.A. Rould, T.A. Steitz, M.A. Rould, J.J. Perona, T.A. Steitz & Biochemistry & 1993 & 32 & 439-449 \\ \hline
ptr003 & 1gtr & Structural basis of anticodon loop recognition by glutaminyl-tRNA synthetase. & M.A. Rould, J.J. Perona, T.A. Steitz & Nature & 1991 & 352 & 8758-8771 \\ \hline
ptr004 & 1ser & The 2.9 A crystal structure of T. thermophilus seryl-tRNA synthetase complexed with tRNA(Ser). & V. Biou, A. Yaremchuk, M. Tukalo, S. Cusack, H. Belrhali, A.D. Yaremchuk, M.A. Tukalo, K. Larsen, C. Berthet-Colominas, R. Leberman, B. Beijer, B. Sproat, J. Als-Nielsen, G. Grubel, J.-F. Legrand, M. Lehmann, S. Cusack, M. Fujinaga, C. Berthet-Colominas, A.D. Yaremchuk, M.A. Tukalo, S. Cusack, S. Price, S. Cusack, F. Borel, C. Berthet-Colominas, R. Leberman, A.D. Yaremchuk, M.A. Tukalo, I. Krikliviy, N. Malchenko, V. Biou, Colominas, name="Berthet- S. Cusack, A.D. Yaremchuk, M.A. Tukalo, I. Krikliviy, V.N. Mel\&apos;nik, C. Berthet-Colominas, S. Cusack, R. Leberman, S. Cusack, M. Hartlein, R. Leberman, S. Cusack, C. Berthet-Colominas, M. Hartlein, N. Nassar, R. Leberman, M.B. Garber, A.D. Yaremchuk, M.A. Tukalo, S.P. Egorova, C. Berthet-Colominas, R. Leberman & Science & 1994 & 263 & 213-218 \\ \hline
ptr009 & 1qrs & Crystal structures of three misacylating mutants of Escherichia coli glutaminyl-tRNA synthetase complexed with tRNA(Gln) and ATP. & J.G. Arnez, T.A. Steitz, M.A. Rould, J.J. Perona, T.A. Steitz, J.J. Perona, R.N. Swanson, M.A. Rould, T.A. Steitz, D. Soll, M.A. Rould, J.J. Perona, D. Soll, T.A. Steitz, H. Inokuchi, P. Hoben, F. Yamao, H. Ozeki, D. Soll & Biochemistry & 1996 & 35 & 1404-1410 \\ \hline
ptr010 & 1qrt & Crystal structures of three misacylating mutants of Escherichia coli glutaminyl-tRNA synthetase complexed with tRNA(Gln) and ATP. & J.G. Arnez, T.A. Steitz, M.A. Rould, J.J. Perona, T.A. Steitz, J.J. Perona, R.N. Swanson, M.A. Rould, T.A. Steitz, D. Soll, M.A. Rould, J.J. Perona, D. Soll, T.A. Steitz, H. Inokuchi, P. Hoben, F. Yamao, H. Ozeki, D. Soll & Biochemistry & 1996 & 35 & 14725-14733 \\ \hline
ptr011 & 1qru & Crystal structures of three misacylating mutants of Escherichia coli glutaminyl-tRNA synthetase complexed with tRNA(Gln) and ATP. & J.G. Arnez, T.A. Steitz, M.A. Rould, J.J. Perona, T.A. Steitz, J.J. Perona, R.N. Swanson, M.A. Rould, T.A. Steitz, D. Soll, M.A. Rould, J.J. Perona, D. Soll, T.A. Steitz, H. Inokuchi, P. Hoben, F. Yamao, H. Ozeki, D. Soll & Biochemistry & 1996 & 35 & 14725-14733 \\ \hline
ptr012 & 1ttt & Crystal structure of the ternary complex of Phe-tRNAPhe, EF-Tu, and a GTP analog. & P. Nissen, M. Kjeldgaard, S. Thirup, G. Polekhina, L. Reshetnikova, B.F. Clark, J. Nyborg, P. Nissen, L. Reshetnikova, G. Siboska, G. Polekhina, S. Thirup, M. Kjeldgaard, B.F. Clark, J. Nyborg, M. Kjeldgaard, P. Nissen, S. Thirup, J. Nyborg & Science & 1995 & 270 & 14725-14733 \\ \hline
ptr016 & 1a9n & Crystal structure of the spliceosomal U2B\&quot;-U2A\&apos; protein complex bound to a fragment of U2 small nuclear RNA. & S.R. Price, P.R. Evans, K. Nagai & Nature & 1998 & 394 & 1464-1472 \\ \hline
rr0005 & 1dk1 & Crystal structure of the S15-rRNA complex. & A. Nikulin, A. Serganov, E. Ennifar, S. Tishchenko, N. Nevskaya, W. Shepard, C. Portier, M. Garber, B. Ehresmann, C. Ehresmann, S. Nikonov, P. Dumas & Nat.Struct.Biol. & 2000 & 7 & 645-650 \\ \hline
rr0009 & 1mms & A detailed view of a ribosomal active site: the structure of the L11-RNA complex. & B.T. Wimberly, R. Guymon, J.P. McCutcheon, S.W. White, V. Ramakrishnan, Y. Xing, D. Draper, J. Thompson, F. Schmidt, E. Cundliffe, J. Thompson, E. Cundliffe, M. Stark & Cell & 1999 & 97 & 273-277 \\ \hline
rr0010 & 1f7y & The crystal structure of UUCG tetraloop. & E. Ennifar, A. Nikulin, S. Tishchenko, A. Serganov, N. Nevskaya, M. Garber, B. Ehresmann, C. Ehresmann, S. Nikonov, P. Dumas & J.Mol.Biol. & 2000 & 304 & 491-502 \\ \hline
rr0012 & 1feu & Structure of ribosomal protein TL5 complexed with RNA provides new insights into the CTC family of stress proteins. & R. Fedorov, V. Meshcheryakov, G. Gongadze, N. Fomenkova, N. Nevskaya, M. Selmer, M. Laurberg, O. Kristensen, S. Al-Karadaghi, A. Liljas, M. Garber, S. Nikonov & Acta Crystallogr.,Sect.D & 2001 & 57 & 35-42 \\ \hline
rr0014 & 1fg0 & The structural basis of ribosome activity in peptide bond synthesis. & P. Nissen, J. Hansen, N. Ban, P.B. Moore, T.A. Steitz, N Ban, P. Nissen, J. Hansen, P.B. Moore, T.A. Steitz, N. Ban, P. Nissen, J. Hansen, M. Capel, P.B. Moore, T.A. Steitz & Science & 2000 & 289 & 968-976 \\ \hline
rr0019 & 1g1x & Structure of the S15,S6,S18-rRNA complex: assembly of the 30S ribosome central domain. & S.C. Agalarov, Prasad, name="Sridhar P.M. Funke, C.D. Stout, J.R. Williamson & Science & 2000 & 288 & 920-930 \\ \hline
rr0050 & 1kuq & Role of N-terminal helix in interaction of ribosomal protein S15 with 16S rRNA. & S.V. Revtovich, A.D. Nikulin, S.V. Nikonov, A. Nikulin, A. Serganov, E. Ennifar, S. Tishchenko, N. Nevskaya, W. Shepard, C. Portier, M. Garber, B. Ehresmann, C. Ehresmann, S. Nikonov, P. Dumas & Biochemistry Mosc. & 2004 & 69 & 107-112 \\ \hline
rr0067 & 1nkw & High resolution structure of the large ribosomal subunit from a mesophilic eubacterium & J.M. Harms, F. Schluenzen, R. Zarivach, A. Bashan, S. Gat, I. Agmon, H. Bartels, F. Franceschi, A. Yonath, F. Schluenzen, R. Zarivach, J.M. Harms, A. Bashan, A. Tocilj, R. Albrecht, A. Yonath, F. Franceschi & Cell (Cambridge,Mass.) & 2001 & 107 & 1319-1323 \\ \hline
rr0110 & 1vqo & Structural Insights into the Roles of Water and the 2\&apos; Hydroxyl of the P Site tRNA in the Peptidyl Transferase Reaction. & T.M. Schmeing, K.S. Huang, D.E. Kitchen, S.A. Strobel, T.A. Steitz & Mol.Cell & 2005 & 20 & 679-688 \\ \hline
rr0143 & 1vs5 & Structural analysis of kasugamycin inhibition of translation. & B.S. Schuwirth, J.M. Day, C.W. Hau, G.R. Janssen, A.E. Dahlberg, J.H.D. Cate, A. Vila-Sanjurjo & Nat.Struct.Mol.Biol. & 2006 & 13 & 437-448 \\ \hline
rr0144 & 1vs6 & Structural analysis of kasugamycin inhibition of translation. & B.S. Schuwirth, J.M. Day, C.W. Hau, G.R. Janssen, A.E. Dahlberg, J.H.D. Cate, A. Vila-Sanjurjo & Nat.Struct.Mol.Biol. & 2006 & 13 & 879-886 \\ \hline
rr0153 & 2j00 & Structure of the 70S ribosome complexed with mRNA and tRNA. & M. Selmer, C.M. Dunham, F.V. Murphy, A. Weixlbaumer, S. Petry, A.C. Kelley, J.R. Weir, V. Ramakrishnan & Science & 2006 & 313 & 879-886 \\ \hline
rr0154 & 2j01 & Structure of the 70S ribosome complexed with mRNA and tRNA. & M. Selmer, C.M. Dunham, F.V. Murphy, A. Weixlbaumer, S. Petry, A.C. Kelley, J.R. Weir, V. Ramakrishnan & Science & 2006 & 313 & 1935-1942 \\ \hline
tr0001 & 1ehz & The crystal structure of yeast phenylalanine tRNA at 1.93 A resolution: a classic structure revisited & H. Shi, P.B. Moore & RNA & 2000 & 6 & 1935-1942 \\ \hline
tr0002 & 1evv & The crystal structure of yeast phenylalanine tRNA at 2.0 A resolution: cleavage by Mg(2+) in 15-year old crystals. & L. Jovine, S. Djordjevic, D. Rhodes, J.E. Ladner, J.T. Finch, A. Klug, B.F. Clark, J.D. Robertus, J.E. Ladner, J.T. Finch, D. Rhodes, R.S. Brown, B.F.C. Clark, A. Klug, J.E. Ladner, A. Jack, J.D. Robertus, R.S. Brown, D. Rhodes, B.F. Clark, A. Klug, B. Hingerty, R.S. Brown, A. Jack, E. Westhof, M. Sundaralingam, E. Westhof, P. Dumas, D. Moras & J.Mol.Biol. & 2000 & 301 & 1091-1105 \\ \hline
tr0003 & 1fir & The crystal structure of HIV reverse-transcription primer tRNA(Lys,3) shows a canonical anticodon loop. & P. Benas, G. Bec, G. Keith, R. Marquet, C. Ehresmann, B. Ehresmann, P. Dumas, P. Benas, P. Dumas, P. Benas & RNA & 2000 & 6 & 401-414 \\ \hline
tr0004 & 1i9v & Aminoglycoside binding displaces a divalent metal ion in a tRNA-neomycin B complex. & N.E. Mikkelsen, K. Johansson, A. Virtanen, L.A. Kirsebom & Nat.Struct.Biol. & 2001 & 8 & 1347-1355 \\ \hline
trna03 & 1tn2 & Crystallographic and biochemical investigation of the lead(II)-catalyzed hydrolysis of yeast phenylalanine tRNA. & R.S. Brown, J.C. Dewan, A. Klug, R.S. Brown, B.E. Hingerty, J.C. Dewan, A. Klug & Biochemistry & 1985 & 24 & 510-514 \\ \hline
trna04 & 6tna & Crystal structure of yeast phenylalanine transfer RNA. I. Crystallographic refinement. & J.L. Sussman, S.R. Holbrook, R.W. Warrant, G.M. Church, S.H. Kim, S.R. Holbrook, J.L. Sussman, R.W. Warrant, S.-H. Kim, S.-H. Kim, A. Rich, S.H. Kim, S.-H. Kim, S.R. Holbrook, J.L. Sussman, R.W. Warrant, G.M. Church, S.-H. Kim, J.L. Sussman, S.-H. Kim, J.L. Sussman, S.-H. Kim & J.Mol.Biol. & 1978 & 123 & 4785-4801 \\ \hline
trna05 & trna05 & Three-Dimensional Structure of Yeast T-RNA-ASP. I. Structure Determination & M.B. Comarmond, R. Giege, J.C. Thierry, D. Moras, J. Fischer & Acta Crystallogr.,Sect.B & 1986 & 42 & 272-280 \\ \hline
trna06 & 1tra & Restrained refinement of the monoclinic form of yeast phenylalanine transfer RNA. Temperature factors and dynamics, coordinated waters, and base-pair propeller twist angles. & E. Westhof, M. Sundaralingam, C.D. Stout, H. Mizuno, S.T. Rao, P. Swaminathan, J. Rubin, T. Brennan, M. Sundaralingam, C.D. Stout, H. Mizuno, J. Rubin, T. Brennan, S.T. Rao, M. Sundaralingam, M. Sundaralingam, H. Mizuno, C.D. Stout, S.T. Rao, M. Liebman, N. Yathindra, T. Ichikawa, M. Sundaralingam & Biochemistry & 1986 & 25 & 607-630 \\ \hline
trna07 & 2tra & Restrained refinement of two crystalline forms of yeast aspartic acid and phenylalanine transfer RNA crystals. & E. Westhof, P. Dumas, D. Moras, E. Westhof, P. Dumas, D. Moras, M.B. Comarmond, R. Giege, J.C. Thierry, D. Moras, J. Fischer, D. Moras, A.-C. Dock, P. Dumas, E. Westhof, P. Romby, J.-P. Ebel, R. Giege, E. Westhof, P. Dumas, D. Moras, P. Dumas, J.P. Ebel, R. Giege, D. Moras, J.C. Thierry, E. Westhof, E. Westhof, P. Dumas, D. Moras, D. Moras, M.B. Comarmond, J. Fischer, R. Weiss, J.C. Thierry, J.P. Ebel, R. Giege, R. Giege, D. Moras, J.C. Thierry & Acta Crystallogr., Sect.A & 1988 & 44 & 4868-4878 \\ \hline
trna08 & 3tra & Restrained refinement of two crystalline forms of yeast aspartic acid and phenylalanine transfer RNA crystals. & E. Westhof, P. Dumas, D. Moras, E. Westhof, P. Dumas, D. Moras, M.B. Comarmond, R. Giege, J.C. Thierry, D. Moras, J. Fischer, D. Moras, A.-C. Dock, P. Dumas, E. Westhof, P. Romby, J.-P. Ebel, R. Giege, E. Westhof, P. Dumas, D. Moras, P. Dumas, J.P. Ebel, R. Giege, D. Moras, J.C. Thierry, E. Westhof, E. Westhof, P. Dumas, D. Moras, D. Moras, M.B. Comarmond, J. Fischer, R. Weiss, J.C. Thierry, J.P. Ebel, R. Giege, R. Giege, D. Moras, J.C. Thierry & Acta Crystallogr., Sect.A & 1988 & 44 & 112-123 \\ \hline
trna09 & 4tra & Restrained refinement of two crystalline forms of yeast aspartic acid and phenylalanine transfer RNA crystals. & E. Westhof, P. Dumas, D. Moras, E. Westhof, P. Dumas, D. Moras, J.L. Sussman, S.R. Holbrook, R.W. Warrant, G.M. Church, S.-H. Kim, S.R. Holbrook, J.L. Sussman, R.W. Warrant, S.-H. Kim, S.-H. Kim, A. Rich, S.H. Kim, S.-H. Kim, S.R. Holbrook, J.L. Sussman, R.W. Warrant, G.M. Church, S.-H. Kim, J.L. Sussman, S.-H. Kim, J.L. Sussman, S.-H. Kim & Acta Crystallogr., Sect.A & 1988 & 44 & 112-123 \\ \hline
trna10 & 4tna & Further refinement of the structure of yeast tRNAPhe. & B. Hingerty, R.S. Brown, A. Jack, A. Jack, M. Levitt, A. Jack, J.E. Ladner, D. Rhodes, R.S. Brown, A. Klug, A. Jack, J.E. Ladner, A. Klug, J.E. Ladner, A. Jack, J.D. Robertus, R.S. Brown, D. Rhodes, B.F.C. Clark, A. Klug, J.D. Robertus, J.E. Ladner, J.T. Finch, D. Rhodes, R.S. Brown, B.F.C. Clark, A. Klug & J.Mol.Biol. & 1978 & 124 & 112-123 \\ \hline
trna12 & 1yfg & The 3 A crystal structure of yeast initiator tRNA: functional implications in initiator/elongator discrimination. & R. Basavappa, P.B. Sigler, R.W. Schevitz, A.D. Podjarny, N. Krishnamachari, J.J. Hughes, P.B. Sigler, J.L. Sussman & EMBO J. & 1991 & 10 & 523-534 \\ \hline
ur0001 & 429d & Crystal structure of a lead-dependent ribozyme revealing metal binding sites relevant to catalysis. & J.E. Wedekind, D.B. McKay & Nat.Struct.Biol. & 1999 & 6 & 3105-3111 \\ \hline
ur0002 & 430d & Crystal structure of the ribosomal RNA domain essential for binding elongation factors. & C.C. Correll, A. Munishkin, Y.L. Chan, Z. Ren, I.G. Wool, T.A. Steitz, A.A. Szewczak, P.B. Moore, Y.L. Chan, I.G. Wool, A.A. Szewczak, P.B. Moore, J.P. Rife, S.C. Stallings, C.C. Correll, A. Dallas, T.A. Steitz, P.B. Moore & Proc.Natl.Acad.Sci.USA & 1998 & 95 & 261-268 \\ \hline
ur0004 & 437d & Minor groove RNA triplex in the crystal structure of a ribosomal frameshifting viral pseudoknot. & L. Su, L. Chen, M. Egli, J.M. Berger, A. Rich & Nat.Struct.Biol. & 1999 & 6 & 13436-13441 \\ \hline
ur0005 & 462d & The crystal structure of the dimerization initiation site of genomic HIV-1 RNA reveals an extended duplex with two adenine bulges. & E. Ennifar, M. Yusupov, P. Walter, R. Marquet, B. Ehresmann, C. Ehresmann, P. Dumas & Structure Fold.Des. & 1999 & 7 & 285-292 \\ \hline
ur0006 & 480d & The two faces of the Escherichia coli 23 S rRNA sarcin/ricin domain: the structure at 1.11 A resolution. & C.C. Correll, I.G. Wool, A. Munishkin, C.C. Correll, A. Munishkin, Y.-L. Chan, Z. Ren, I.G. Wool, J.P. Rife, S.G. Stallings, C.C. Correll, A. Dallas, T.A. Steitz, P.B. Moore, A.A. Szewczak, P.B. Moore, A.A. Szewczak, P.B. Moore & J.Mol.Biol. & 1999 & 292 & 1439-1449 \\ \hline
ur0007 & 483d & The two faces of the Escherichia coli 23 S rRNA sarcin/ricin domain: the structure at 1.11 A resolution. & C.C. Correll, I.G. Wool, A. Munishkin, C.C. Correll, A. Munishkin, Y.-L. Chan, Z. Ren, I.G. Wool, J.P. Rife, S.G. Stallings, C.C. Correll, A. Dallas, T.A. Steitz, P.B. Moore, A.A. Szewczak, P.B. Moore, A.A. Szewczak, P.B. Moore & J.Mol.Biol. & 1999 & 292 & 275-287 \\ \hline
ur0008 & 1ddy & The structural basis for molecular recognition by the vitamin B 12 RNA aptamer. & D. Sussman, J.C. Nix, C. Wilson & Nat.Struct.Biol. & 2000 & 7 & 275-287 \\ \hline
ur0010 & 488d & Capture and visualization of a catalytic RNA enzyme-product complex using crystal lattice trapping and X-ray holographic reconstruction. & J.B. Murray, H. Szoke, A. Szoke, W.G. Scott & Mol.Cell & 2000 & 5 & 53-57 \\ \hline
ur0011 & 1f1t & 2.8 A crystal structure of the malachite green aptamer. & C. Baugh, D. Grate, C. Wilson & J.Mol.Biol. & 2000 & 301 & 279-287 \\ \hline
ur0012 & 1hr2 & Structural basis of the enhanced stability of a mutant ribozyme domain and a detailed view of RNA--solvent interactions. & K. Juneau, E. Podell, D.J. Harrington, T.R. Cech, K. Juneau, T.R. Cech, J.H. Cate, A.R. Gooding, E. Podell, K. Zhou, B.L. Golden, C.E. Kundrot, T.R. Cech, Doudna, name="A J.H. Cate, J.A. Doudna, J.H. Cate, R.L. Hanna, J.A. Doudna & Structure & 2001 & 9 & 117-128 \\ \hline
ur0017 & 1k9w & Crystal structures of coaxially stacked kissing complexes of the HIV-1 RNA dimerization initiation site. & E. Ennifar, P. Walter, B. Ehresmann, C. Ehresmann, P. Dumas & Nat.Struct.Biol. & 2001 & 8 & 221-231 \\ \hline
ur0018 & 1kh6 & Crystal structure of an RNA tertiary domain essential to HCV IRES-mediated translation initiation. & J.S. Kieft, K. Zhou, A. Grech, R. Jubin, J.A. Doudna & Nat.Struct.Biol. & 2002 & 9 & 1064-1068 \\ \hline
ur0019 & 1kxk & Structural insights into group II intron catalysis and branch-site selection. & L. Zhang, J.A. Doudna & Science & 2002 & 295 & 370-374 \\ \hline
ur0020 & 1l2x & Metal ions and flexibility in a viral RNA pseudoknot at atomic resolution. & M. Egli, G. Minasov, L. Su, A. Rich & Proc.Natl.Acad.Sci.USA & 2002 & 99 & 2084-2088 \\ \hline
ur0021 & 1l3d & Metal ions and flexibility in a viral RNA pseudoknot at atomic resolution. & M. Egli, G. Minasov, L. Su, A. Rich & Proc.Natl.Acad.Sci.USA & 2002 & 99 & 4302-4307 \\ \hline
ur0022 & 1l8v & Specificity of RNA-RNA Helix Recognition & D.J. Battle, J.A. Doudna & Proc.Natl.Acad.Sci.USA & 2002 & 99 & 4302-4307 \\ \hline
ur0025 & 1mhk & The crystal structure of a 26-nucleotide RNA containing a hook-turn & S. Szep, J. Wang, P.B. Moore & RNA & 2003 & 9 & 11676-11681 \\ \hline
ur0026 & 1msy & Common and distinctive features of GNRA tetraloops based on a GUAA tetraloop structure at 1.4 A resolution & C.C. Correll, K. Swinger & RNA & 2003 & 9 & 44-51 \\ \hline
ur0027 & 1nbs & Crystal structure of the specificity domain of Ribonuclease P & A.S. Krasilnikov, X. Yang, T. Pan, A. Mondragon & Nature & 2003 & 421 & 355-363 \\ \hline
ur0028 & 1nuj & Crystal structure of the leadzyme at 1.8 A resolution: metal ion binding and the implications & J.E. Wedekind, D.B. McKay, J.E. Wedekind, D.B. McKay & BIOCHEMISTRY & 2003 & 42 & 760-764 \\ \hline
ur0029 & 1nyi & A helical twist-induced conformational switch activates cleavage in the hammerhead ribozyme. & C.M. Dunham, J.B. Murray, W.G. Scott & J.Mol.Biol. & 2003 & 332 & 9554-9563 \\ \hline
ur0030 & 1nuv & Crystal structure of the leadzyme at 1.8 A resolution: metal ion binding and the implications & J.E. Wedekind, D.B. McKay, J.E. Wedekind, D.B. McKay & BIOCHEMISTRY & 2003 & 42 & 327-336 \\ \hline
ur0032 & 1q29 & A helical twist-induced conformational switch activates cleavage in the hammerhead ribozyme. & C.M. Dunham, J.B. Murray, W.G. Scott & J.Mol.Biol. & 2003 & 332 & 9554-9563 \\ \hline
ur0033 & 1q93 & The common and distinctive features of the bulged-G motif based on a 1.04 A resolution RNA structure & C.C. Correll, J. Beneken, M.J. Plantinga, M. Lubbers, Y.L. Chan & Nucleic Acids Res. & 2003 & 31 & 327-336 \\ \hline
ur0034 & 1q96 & The common and distinctive features of the bulged-G motif based on a 1.04 A resolution RNA structure & C.C. Correll, J. Beneken, M.J. Plantinga, M. Lubbers, Y.L. Chan & Nucleic Acids Res. & 2003 & 31 & 6806-6818 \\ \hline
ur0035 & 1q9a & The common and distinctive features of the bulged-G motif based on a 1.04 A resolution RNA structure & C.C. Correll, J. Beneken, M.J. Plantinga, M. Lubbers, Y.L. Chan & Nucleic Acids Res. & 2003 & 31 & 6806-6818 \\ \hline
ur0036 & 1r3o & First look at RNA in L-configuration. & M. Vallazza, M. Perbandt, S. Klussmann, W. Rypniewski, H.M. Einspahr, V.A. Erdmann, C.h. Betzel & Acta Crystallogr.,Sect.D & 2004 & 60 & 6806-6818 \\ \hline
ur0037 & 1t0d & Monitoring molecular recognition of the ribosomal decoding site. & S. Shandrick, Q. Zhao, Q. Han, B.K. Ayida, M. Takahashi, G.C. Winters, K.B. Simonsen, D. Vourloumis, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2004 & 43 &  \\ \hline
ur0038 & 1t0e & Monitoring molecular recognition of the ribosomal decoding site. & S. Shandrick, Q. Zhao, Q. Han, B.K. Ayida, M. Takahashi, G.C. Winters, K.B. Simonsen, D. Vourloumis, T. Hermann & Angew.Chem.Int.Ed.Engl. & 2004 & 43 & 3177-3182 \\ \hline
ur0039 & 1u8d & Structure of a natural guanine-responsive riboswitch complexed with the metabolite hypoxanthine. & R.T. Batey, S.D. Gilbert, R.K. Montange & Nature & 2004 & 432 & 3177-3182 \\ \hline
ur0040 & 1u9s & Basis for structural diversity in homologous RNAs. & A.S. Krasilnikov, Y. Xiao, T. Pan, A. Mondragon & Science & 2004 & 306 & 411-415 \\ \hline
ur0042 & 1x9c & Conformational Heterogeneity at Position U37 of an All-RNA Hairpin Ribozyme with Implications for Metal Binding and the Catalytic Structure of the S-Turn. & S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind & Biochemistry & 2005 & 44 & 104-107 \\ \hline
ur0043 & 1x9k & Conformational Heterogeneity at Position U37 of an All-RNA Hairpin Ribozyme with Implications for Metal Binding and the Catalytic Structure of the S-Turn. & S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind & Biochemistry & 2005 & 44 & 14396-14408 \\ \hline
ur0044 & 1xjr & The structure of a rigorously conserved RNA element within the SARS virus genome & M.P. Robertson, H. Igel, R. Baertsch, D. Haussler, Jr., name="Ares W.G. Scott & Plos Biol. & 2005 & 3 & 14396-14408 \\ \hline
ur0045 & 1xp7 & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 86-94 \\ \hline
ur0046 & 1xpe & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 771-782 \\ \hline
ur0047 & 1xpf & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 771-782 \\ \hline
ur0049 & 1y3o & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies. & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 771-782 \\ \hline
ur0050 & 1y3s & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies. & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 771-782 \\ \hline
ur0051 & 1y26 & Structural Basis for Discriminative Regulation of Gene Expression by Adenine- and Guanine-Sensing mRNAs & A. Serganov, Y.R. Yuan, O. Pikovskaya, A. Polonskaia, L. Malinina, A.T. Phan, C. Hobartner, R. Micura, R.R. Breaker, D.J. Patel & Chem.Biol. & 2004 & 11 & 771-782 \\ \hline
ur0052 & 1y27 & Structural Basis for Discriminative Regulation of Gene Expression by Adenine- and Guanine-Sensing mRNAs & A. Serganov, Y.R. Yuan, O. Pikovskaya, A. Polonskaia, L. Malinina, A.T. Phan, C. Hobartner, R. Micura, R.R. Breaker, D.J. Patel & Chem.Biol. & 2004 & 11 & 1729-1741 \\ \hline
ur0053 & 1ykq & Structural basis for Diels-Alder ribozyme-catalyzed carbon-carbon bond formation. & A. Serganov, S. Keiper, L. Malinina, V. Tereshko, E. Skripkin, C. Hobartner, A. Polonskaia, A.T. Phan, R. Wombacher, R. Micura, Z. Dauter, A. Jaschke, D.J. Patel & Nat.Struct.Mol.Biol. & 2005 & 12 & 1729-1741 \\ \hline
ur0054 & 1ykv & Structural basis for Diels-Alder ribozyme-catalyzed carbon-carbon bond formation. & A. Serganov, S. Keiper, L. Malinina, V. Tereshko, E. Skripkin, C. Hobartner, A. Polonskaia, A.T. Phan, R. Wombacher, R. Micura, Z. Dauter, A. Jaschke, D.J. Patel & Nat.Struct.Mol.Biol. & 2005 & 12 & 218-224 \\ \hline
ur0055 & 1yls & Structural basis for Diels-Alder ribozyme-catalyzed carbon-carbon bond formation. & A. Serganov, S. Keiper, L. Malinina, V. Tereshko, E. Skripkin, C. Hobartner, A. Polonskaia, A.T. Phan, R. Wombacher, R. Micura, Z. Dauter, A. Jaschke, D.J. Patel & Nat.Struct.Mol.Biol. & 2005 & 12 & 218-224 \\ \hline
ur0056 & 1z43 & Structural insights into SRP RNA: An induced fit mechanism for SRP assembly & T. Hainzl, S. Huang, A.E. Sauer-Eriksson, T. Hainzl, S. Huang, A.E. Sauer-Eriksson & Rna & 2005 & 11 & 218-224 \\ \hline
ur0057 & 1yxp & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies. & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 1043-1050 \\ \hline
ur0058 & 1zci & Polymorphism of Bulged-out Residues in HIV-1 RNA DIS Kissing Complex and Structure Comparison with Solution Studies. & E. Ennifar, P. Dumas & J.Mol.Biol. & 2006 & 356 & 771-782 \\ \hline
ur0060 & 1zft & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind, R. Pinard, K.J. Hampel, J.E. Heckman, D. Lambert, P.A. Chan, F. Major, J.M. Burke & Biochemistry & 2006 & 45 & 771-782 \\ \hline
ur0061 & 1zfv & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind, R. Pinard, K.J. Hampel, J.E. Heckman, D. Lambert, P.A. Chan, F. Major, J.M. Burke & Biochemistry & 2006 & 45 & 686-700 \\ \hline
ur0062 & 1zfx & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind, R. Pinard, K.J. Hampel, J.E. Heckman, D. Lambert, P.A. Chan, F. Major, J.M. Burke & Biochemistry & 2006 & 45 & 686-700 \\ \hline
ur0065 & 2a64 & Crystal structure of a bacterial ribonuclease P RNA. & A.V. Kazantsev, A.A. Krivenko, D.J. Harrington, S.R. Holbrook, P.D. Adams, N.R. Pace & Proc.Natl.Acad.Sci.Usa & 2005 & 102 & 686-700 \\ \hline
ur0066 & 2a43 & Crystal Structure of a Luteoviral RNA Pseudoknot and Model for a Minimal Ribosomal Frameshifting Motif & P.S. Pallan, W.S. Marshall, J. Harp, III, name="Jewett Z. Wawrzak, II, name="Brown A. Rich, M. Egli & Biochemistry & 2005 & 44 & 13392-13397 \\ \hline
ur0068 & 2d2k & Conformational heterogeneity at position U37 of an all-RNA hairpin ribozyme with implications for metal binding and the catalytic structure of the S-turn & S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind & Biochemistry & 2005 & 44 & 11315-11322 \\ \hline
ur0069 & 2d2l & Conformational heterogeneity at position U37 of an all-RNA hairpin ribozyme with implications for metal binding and the catalytic structure of the S-turn & S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind & Biochemistry & 2005 & 44 & 14396-14408 \\ \hline
ur0070 & 2b57 & Thermodynamic and kinetic characterization of ligand binding to the purine riboswitch aptamer domain. & S.D. Gilbert, C.D. Stoddard, S.J. Wise, R.T. Batey & J.Mol.Biol. & 2006 & 359 & 14396-14408 \\ \hline
ur0071 & 2b8r & Crystal structures of coaxially stacked kissing complexes of the HIV-1 RNA dimerization initiation site & E. Ennifar, P. Walter, B. Ehresmann, C. Ehresmann, P. Dumas & Nat.Struct.Biol. & 2001 & 8 & 754-768 \\ \hline
ur0072 & 2b8s & Crystal structures of coaxially stacked kissing complexes of the HIV-1 RNA dimerization initiation site & E. Ennifar, P. Walter, B. Ehresmann, C. Ehresmann, P. Dumas & NAT.STRUCT.BIOL. & 2001 & 8 & 1064-1068 \\ \hline
ur0074 & 2bcy & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J.D. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind & Biochemistry & 2006 & 45 & 1064-1068 \\ \hline
ur0075 & 2bcz & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J.D. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind & Biochemistry & 2006 & 45 & 686-700 \\ \hline
ur0076 & 2fgp & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J.D. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind, V. Grum-Tokars, M Milovanovic, J.E. Wedekind & Biochemistry & 2006 & 45 & 686-700 \\ \hline
ur0078 & 2gcs & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 686-700 \\ \hline
ur0079 & 2gcv & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 1752-1756 \\ \hline
ur0081 & 2gdi & Structural basis for gene regulation by a thiamine pyrophosphate-sensing riboswitch. & A. Serganov, A. Polonskaia, A.T. Phan, R.R. Breaker, D.J. Patel & Nature & 2006 & 441 & 1752-1756 \\ \hline
ur0082 & 2gis & Structure of the S-adenosylmethionine riboswitch regulatory mRNA element. & R.K. Montange, R.T. Batey & Nature & 2006 & 441 & 1167-1171 \\ \hline
ur0084 & 2goz & Tertiary Contacts Distant from the Active Site Prime a Ribozyme for Catalysis. & M. Martick, W.G. Scott & Cell & 2006 & 126 & 1172-1175 \\ \hline
ur0090 & 2grb & Crystal structure of an RNA quadruplex containing inosine tetrad: implications for the roles of NH2 group in purine tetrads. & B. Pan, K. Shi, M. Sundaralingam & J.Mol.Biol. & 2006 & 363 & 309-320 \\ \hline
ur0091 & 2h0s & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 451-459 \\ \hline
ur0092 & 2h0w & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 1752-1756 \\ \hline
ur0093 & 2h0x & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 1752-1756 \\ \hline
ur0094 & 2h0z & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 1752-1756 \\ \hline
ur0095 & 2g9c & Modified pyrimidines specifically bind the purine riboswitch. & S.D. Gilbert, S.J. Mediatore, R.T. Batey & J.Am.Chem.Soc. & 2006 & 128 & 1752-1756 \\ \hline
ur0096 & 2ho6 & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 14214-14215 \\ \hline
ur0097 & 2ho7 & Structural basis of glmS ribozyme activation by glucosamine-6-phosphate & D.J. Klein, A.R. Ferre-D\&apos;Amare & Science & 2006 & 313 & 1752-1756 \\ \hline
ur0098 & 2cky & Structure of the eukaryotic thiamine pyrophosphate riboswitch with its regulatory ligand. & S. Thore, M. Leibundgut, N. Ban & Science & 2006 & 312 & 1752-1756 \\ \hline
ur0099 & 2hoj & Crystal Structures of the Thi-Box Riboswitch Bound to Thiamine Pyrophosphate Analogs Reveal Adaptive RNA-Small Molecule Recognition & T.E. Edwards, A.R. Ferre-D\&apos;Amare & Structure & 2006 & 14 & 1208-1211 \\ \hline
ur0100 & 2hok & Crystal Structures of the Thi-Box Riboswitch Bound to Thiamine Pyrophosphate Analogs Reveal Adaptive RNA-Small Molecule Recognition & T.E. Edwards, A.R. Ferre-D\&apos;Amare & Structure & 2006 & 14 & 1459-1468 \\ \hline
ur0101 & 2hol & Crystal Structures of the Thi-Box Riboswitch Bound to Thiamine Pyrophosphate Analogs Reveal Adaptive RNA-Small Molecule Recognition & T.E. Edwards, A.R. Ferre-D\&apos;Amare & Structure & 2006 & 14 & 1459-1468 \\ \hline
ur0102 & 2hom & Crystal Structures of the Thi-Box Riboswitch Bound to Thiamine Pyrophosphate Analogs Reveal Adaptive RNA-Small Molecule Recognition & T.E. Edwards, A.R. Ferre-D\&apos;Amare & Structure & 2006 & 14 & 1459-1468 \\ \hline
ur0103 & 2hoo & Crystal Structures of the Thi-Box Riboswitch Bound to Thiamine Pyrophosphate Analogs Reveal Adaptive RNA-Small Molecule Recognition & T.E. Edwards, A.R. Ferre-D\&apos;Amare & Structure & 2006 & 14 & 1459-1468 \\ \hline
ur0104 & 2hop & Crystal Structures of the Thi-Box Riboswitch Bound to Thiamine Pyrophosphate Analogs Reveal Adaptive RNA-Small Molecule Recognition & T.E. Edwards, A.R. Ferre-D\&apos;Amare & Structure & 2006 & 14 & 1459-1468 \\ \hline
ur0105 & 2il9 & Structural basis for ribosome recruitment and manipulation by a viral IRES RNA & J.S. Pfingsten, D.A. Costantino, J.S. Kieft & Science & 2006 & 314 & 1459-1468 \\ \hline
ur0106 & 2npy & A posteriori design of crystal contacts to improve the X-ray diffraction properties of a small RNA enzyme. & C. MacElrevey, R.C. Spitale, J. Krucinska, J.E. Wedekind, J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J. Wedekind, S. Alam, V. Grum-Tokars, J. Krucinska, M. Kundracik, J. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind & Acta Crystallogr.,Sect.D & 2007 & 63 & 1450-1454 \\ \hline
ur0107 & 2npz & A posteriori design of crystal contacts to improve the X-ray diffraction properties of a small RNA enzyme. & C. MacElrevey, R.C. Spitale, J. Krucinska, J.E. Wedekind, J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, S. Alam, V. Grum-Tokars, J. Krucinska, M. Kundracik, J.E. Wedekind, V. Grum-Tokars, M. Milovanovic, J.E. Wedekind & Acta Crystallogr.,Sect.D & 2007 & 63 & 812-825 \\ \hline
ur0108 & 2oeu & Full-length hammerhead ribozyme with Mn(II) bound & M. Martick, W.G. Scott & To be Published & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & 812-825 \\ \hline
ur0109 & 2oue & Water in the Active Site of an All-RNA Hairpin Ribozyme and Effects of Gua8 Base Variants on the Geometry of Phosphoryl Transfer. & J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind & Biochemistry & 2006 & 45 &   \\ \hline
ur0110 & 2oiu & The structural basis of ribozyme-catalyzed RNA assembly. & M.P. Robertson, W.G. Scott & Science & 2007 & 315 & 686-700 \\ \hline
ur0111 & 2ees & Mutational analysis of the purine riboswitch aptamer domain & S.D. Gilbert, C.E. Love, A.L. Edwards, R.T. Batey & Biochemistry & 2007 & 46 & 1549-1553 \\ \hline
ur0112 & 2eet & Mutational analysis of the purine riboswitch aptamer domain & S.D. Gilbert, C.E. Love, A.L. Edwards, R.T. Batey & Biochemistry & 2007 & 46 & 13297-13309 \\ \hline
ur0113 & 2eeu & Mutational analysis of the purine riboswitch aptamer domain & S.D. Gilbert, C.E. Love, A.L. Edwards, R.T. Batey & Biochemistry & 2007 & 46 & 13297-13309 \\ \hline
ur0114 & 2eev & Mutational analysis of the purine riboswitch aptamer domain & S.D. Gilbert, C.E. Love, A.L. Edwards, R.T. Batey & Biochemistry & 2007 & 46 & 13297-13309 \\ \hline
ur0115 & 2eew & Mutational analysis of the purine riboswitch aptamer domain & S.D. Gilbert, C.E. Love, A.L. Edwards, R.T. Batey & Biochemistry & 2007 & 46 & 13297-13309 \\ \hline
ur0118 & 2p7f & A comparison of vanadate to a 2\&apos;-5\&apos; linkage at the active site of a small ribozyme suggests a role for water in transition-state stabilization & A.T. Torelli, J. Krucinska, J.E. Wedekind, J. Salter, J. Krucinska, S. Alam, V. Grum-Tokars, J.E. Wedekind, S. Alam, V. Grum-Tokars, J. Krucinska, M.L. Kundracik, J.E. Wedekind & Rna & 2007 & 13 & 13297-13309 \\ \hline
ur0120 & 2qbz & Structure and mechanism of a metal-sensing regulatory RNA & III, name="Dann C.A. Wakeman, C.L. Sieling, S.C. Baker, I. Irnov, W.C. Winkler & Cell(Cambridge,Mass.) & 2007 & 130 & 1052-1070 \\ \hline
ur0125 & 2qwy & Structure of the SAM-II riboswitch bound to S-adenosylmethionine. & S.D. Gilbert, R.P. Rambo, Tyne, name="Van R.T. Batey & Nat.Struct.Mol.Biol. & 2008 & 15 & 878-892 \\ \hline
ur0126 & 3b4a & Essential Role of an Active-Site Guanine in glmS Ribozyme Catalysis. & D.J. Klein, M.D. Been, A.R. Ferre-D\&apos;Amare & J.Am.Chem.Soc. & 2007 & 129 & 177-182 \\ \hline
ur0127 & 3b4b & Essential Role of an Active-Site Guanine in glmS Ribozyme Catalysis. & D.J. Klein, M.D. Been, A.R. Ferre-D\&apos;Amare & J.Am.Chem.Soc. & 2007 & 129 & 14858-14859 \\ \hline
ur0128 & 3b4c & Essential Role of an Active-Site Guanine in glmS Ribozyme Catalysis. & D.J. Klein, M.D. Been, A.R. Ferre-D\&apos;Amare & J.Am.Chem.Soc. & 2007 & 129 & 14858-14859 \\ \hline
url029 & 205d & Structure of an RNA double helix including uracil-uracil base pairs in an internal loop. & K.J. Baeyens, Bondt, name="De S.R. Holbrook & Nat.Struct.Biol. & 1995 & 2 & 14858-14859 \\ \hline
url050 & 280d & The structure of an RNA dodecamer shows how tandem U-U base pairs increase the range of stable RNA structures and the diversity of recognition sites. & S.E. Lietzke, C.L. Barnes, J.A. Berglund, C.E. Kundrot, S.E. Lietzke, V.E. Carperos, C.E. Kundrot, J.A. Doudna, C. Grosshans, A. Gooding, C.E. Kundrot & Structure & 1996 & 4 & 56-62 \\ \hline
url064 & 354d & Metals, motifs, and recognition in the crystal structure of a 5S rRNA domain. & C.C. Correll, B. Freeborn, P.B. Moore, T.A. Steitz, C.C. Correll, B. Freeborn, P.B. Moore, T.A. Steitz, A. Dallas, P.B. Moore & Cell & 1997 & 91 & 917-930 \\ \hline
url066 & 357d & Metals, motifs, and recognition in the crystal structure of a 5S rRNA domain. & C.C. Correll, B. Freeborn, P.B. Moore, T.A. Steitz, C.C. Correll, B. Freeborn, P.B. Moore, T.A. Steitz, A. Dallas, P.B. Moore & Cell & 1997 & 91 & 705-712 \\ \hline
url069 & 364d & Metals, motifs, and recognition in the crystal structure of a 5S rRNA domain. & C.C. Correll, B. Freeborn, P.B. Moore, T.A. Steitz, C.C. Correll, B. Freeborn, P.B. Moore, T.A. Steitz, A. Dallas, P.B. Moore & Cell & 1997 & 91 & 705-712 \\ \hline
urt068 & 361d & Crystal structure of domain E of Thermus flavus 5S rRNA: a helical RNA structure including a hairpin loop. & M. Perbandt, A. Nolte, S. Lorenz, R. Bald, C. Betzel, V.A. Erdmann & FEBS Lett. & 1998 & 429 & 705-712 \\ \hline
urx035 & 1mme & The crystal structure of an all-RNA hammerhead ribozyme: a proposed mechanism for RNA catalytic cleavage. & W.G. Scott, J.T. Finch, A. Klug & Cell & 1995 & 81 & 211-215 \\ \hline
urx053 & 1gid & Crystal structure of a group I ribozyme domain: principles of RNA packing. & J.H. Cate, A.R. Gooding, E. Podell, K. Zhou, B.L. Golden, C.E. Kundrot, T.R. Cech, J.A. Doudna, J.H. Cate, A.R. Gooding, E. Podell, K. Zhou, B.L. Golden, A.A. Szewczak, C.E. Kundrot, T.R. Cech, J.A. Doudna, J.H. Cate, J.A. Doudna & Science & 1996 & 273 & 991-1002 \\ \hline
urx057 & 299d & Capturing the structure of a catalytic RNA intermediate: the hammerhead ribozyme. & W.G. Scott, J.B. Murray, J.R. Arnold, B.L. Stoddard, A. Klug & Science & 1996 & 274 & 1678-1685 \\ \hline
urx058 & 300d & Capturing the structure of a catalytic RNA intermediate: the hammerhead ribozyme. & W.G. Scott, J.B. Murray, J.R. Arnold, B.L. Stoddard, A. Klug & Science & 1996 & 274 & 2065-2069 \\ \hline
urx059 & 301d & Capturing the structure of a catalytic RNA intermediate: the hammerhead ribozyme. & W.G. Scott, J.B. Murray, J.R. Arnold, B.L. Stoddard, A. Klug & Science & 1996 & 274 & 2065-2069 \\ \hline
urx063 & 353d & Crystal structure of domain A of Thermus flavus 5S rRNA and the contribution of water molecules to its structure. & C. Betzel, S. Lorenz, J.P. Furste, R. Bald, M. Zhang, T.R. Schneider, K.S. Wilson, V.A. Erdmann, M. Perbandt, S. Lorenz, C. Betzel, V.A. Erdmann, S. Lorenz, J. Furste, R. Bald, M. Zhang, E. Raderschall, C. Betzel, Z. Dauter, K. Wilson & FEBS Lett. & 1994 & 351 & 2065-2069 \\ \hline
urx067 & 359d & Inhibition of the hammerhead ribozyme cleavage reaction by site-specific binding of Tb. & A.L. Feig, W.G. Scott, O.C. Uhlenbeck, W.G. Scott, J.B. Murray, J.R.P. Arnold, B.L. Stoddard, A. Klug & Science & 1998 & 279 & 159-164 \\ \hline
urx071 & 379d & The structural basis of hammerhead ribozyme self-cleavage. & J.B. Murray, D.P. Terwey, L. Maloney, A. Karpeisky, N. Usman, L. Beigelman, W.G. Scott & Cell & 1998 & 92 & 81-84 \\ \hline
urx072 & 387d & The Structure of an RNA Pseudoknot Shows 3D Domain Swapping & S.E. Lietzke, C.L. Barnes, V.F. Malone, J.T. Jones, C.E. Kundrot, J.T. Jones, C.L. Barnes, S.E. Lietzke, O. Wieichenrieder, J.A. Doudna, C.E. Kundrot, L. Green, S. Waugh, J.P. Brinkley, Z. Hostomska, C. Tuerk, C. Tuerk, S. MacDougal, L. Gould & Structure, Motion, Interaction and Expression of Biological Macromolecules, The Proceedings of the Tenth Conversation held at The University-SUNY, Albany NY, June 17-21, 1997 & 1998 & 10 & 665-673 \\ \hline
urx075 & 397d & A 1.3-A resolution crystal structure of the HIV-1 trans-activation response region RNA stem reveals a metal ion-dependent bulge conformation. & J.A. Ippolito, T.A. Steitz & Proc.Natl.Acad.Sci.USA & 1998 & 95 & 91-101 \\ \hline
\end{longtable}
\end{center}
\label{tab:helregdb}
\end{landscape}
}
