\chapter{Persistence Length}
\label{appendix4a}
\bibliographystyle{nar}
Nucleic Acids and other polymers, due to their size, can be understood
as  mechanical  objects  \cite{marko2003,  nelson2004}  and  therefore
engineering approaches  can be used for  their understanding.  Usually
the methods followed by  the engineering approach consider the polymer
as a long  continuous rod, and are known  as continuum elastic theory.
This type of  continuous approach leaves little space  for taking into
account the nature of the subunits which make up the polymer, that is,
it  is  mainly  applicable   to  homopolymers  made  up  of  identical
subunits. In  nucleic acids  this is not  necesarily the case,  a more
general approach  should take into  account the possibility  of having
different  subunits making  up the  polymer.  Olson  and collaborators
have  developed  a  sequence   dependent  model,  refered  to  as  the
``realistic'' model  \cite{olson1993}.  Such model  follows a harmonic
approximation and  depends on determination  of force-constant analogs
derived from  X-Ray cristallographic data taken from  the Nucleic Acid
Database (NDB)  \cite{go1976, olson1998}.   Within the context  of the
``realistic'' model Czapla et  al.  \cite{czapla2006} have suggested a
gaussian  sampling  methodology  which  allows us  to  compute  global
polymer  properties like  the  persistence length  following a  matrix
approach  suggested by  Flory  \cite{flory1969} and  expanded upon  by
Olson et al. \cite{maroun1988a, marky1994a}

In what follows we summarize definitions of persistence length and how
it's computed using different models.
%The "realistic model" can be simplified to other  models, for example
%to the  freely rotating model, just by  making the  twisting constant
%zero, that is, the polymer will not be elastic when twisted.

\section{Persistence Length Definition}
%%Perhaps it would be good to say, "parallel and equivalent" perspect.
In  general there  are two  parallel and  analog perspectives  used to
define  the persistence  length  of  polymers. One of these has a  more
intrinsically mathematical,  or physical flavour,  and it's understood
as the resistance to deformation  of; a curve in space (a mathematical
object), or a thin rod (a physical object).  The other is a stochastic
one, where it's  understood as ``a measure of  the distance over which
the direction of the  polymer\footnote{In the original citation DNA is
  used instead of polymer. The citation has been modified here for
  clarity.} is maintained'' \cite{olson1995}.  In both cases the
persistence length definition can be undestood as a measure of polymer
stiffness.

Within the context of the ``physicists'' definition we cite Marko's
and Nelson's definitions:

``Classical elasticity tells us that a thin, straight rod that is bent
into an arc has a bending energy $E=Bl/2R^2$, where $B$ is the bending
elastic constant of the  rod, $l$ is the length of the  rod and $R$ is
the radius  of arc. Setting  $R=l$ gives us  the energy of a  1 radian
bend along the rod, and solving  for when $E \sim K_{B}T$ gives us the
length  of  rod along  which  a thermally  excited  bend  of 1  radian
typically occurs:  $l \sim B/K_{B}T$.  This is  called the persistence
length...'' John F. Marko and Simona Cocco, Physics World, March 2003

``In the elastic rod model of a polymer, the elastic energy of a short
segment       of       rod       is       $dE=\frac{1}{2}       K_{B}T
[A\beta^2+Bu^2+C\omega^2+2Du\omega]  ds$.  Here  $AK_{B}T$, $CK_{B}T$,
$BK_{B}T$,  and $DK_{B}T$  are  the bend  stiffness, twist  stiffness,
stretch stiffness, and twist-stretch coupling, and ds is the length of
the segment.   (The quantities A  and C are  also called the  bend and
twist  persistence  lengths.)''   Philip Nelson,  Biological  Physics:
Energy, Information, Life, 2004.

These definitions coming from the point of view of physicists refer to
an ideal  continuous thin rod.  Marko, refers  to the bend-persistence
length,  whereas Nelson's  definition uses  a more  general  notion of
persistence length which includes besides the bend persistence length,
twist and a stretch persistence lengths.

From the ``stochastic'' perspective we cite Flory's definition:

``the average sum of  the projections of all bonds $ j  \geq i$ on bond
$i$ in an indefinetely long chain.  The bond $i$ is taken to be remote
from either end of  the chain, i.e., $1 \ll i \ll  n$''. Paul J. Flory,
Statistical Mechanics of Chain Molecules. 1969

This  second perspective  is more  familiar to  the chemist,  since it
assumes  some type  of  bonded connectivity  between polymeric  units,
where the bond can be either ``real'', or ``virtual''.

Both perspectives are  analog to one another since  the latter one can
be made to appear like the first in the limit where the length of
the bonds  connecting the monomeric units  is zero, and  the number of
monomers reaches very large numbers, formally, infinity.

When talking about persistence length it's usually difficult to have a
good idea of the meaning of the quantity by itself, that is, if we are
told that the  persistence length of DNA is, say,  530 \AA~ under some
specific concentration and temperature  conditions, we don't know what
this is telling us about its stiffness since we don't know any other
standard values to relate this one to. To give
a better understanding of the meaning of the values of the persistence
length,  we   have  collected  in   Table~\ref{tab:perval}  values  of
persistence  length for various  filamentous biopolymers.   Looking at
Table~\ref{tab:perval}  it's  clear  that   B-DNA  is  quite  a  stiff
biopolymer if compared to poly-glycine, or poly-alanine.

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\begin{tabular}{l|r|c}
\hline
Polymer               & $a$ (nm) & Citation  \\ \hline
Polymethylene         & 0.6      & Flory\tnote{a}      \\  
Polystyrene           & 0.9      & Flory\tnote{a}      \\
Polyglycine           & 0.6      & Flory \tnote{b}     \\
Poly-L-alanine        & 2        & Flory \tnote{b}     \\
Poly-L-proline        & 22       & Cantor and Schimel \cite{cantor1980} \\
B-DNA                 & 53       & Rivetti \cite{rivetti1996}     \\
A-RNA                 & 70-80    & Hagerman  \cite{hagerman1997}  \\
$\alpha$-helix        & 80-100   & Lakkaraju \cite{lakkaraju2009} \\
Coiled-coil           & 150-300  & Lakkaraju \cite{lakkaraju2009} \\
Neurofilament         & 500      & Nelson    \cite{nelson2004}    \\
Intermediate Filament & 1000     & Lakkaraju \cite{lakkaraju2009} \\
F-Actin               & 17000    & Lakkaraju \cite{lakkaraju2009} \\
Microtubule           & 5200000  & Lakkaraju \cite{lakkaraju2009} \\
\hline
\end{tabular}
\begin{tablenotes}
\item [a] Computed using  characteristic ratios reported in Table 1
  of Flory's book \cite{flory1969} with C-C bond length $\nu = 1.54$ \AA.
\item [b] Computed using  characteristic ratios reported in Table 3
  of Flory's book \cite{flory1969} with C$^{\alpha}_{i}$ to C$^{\alpha}_{i+1}$ virtual
  bond length $\nu = 3.80$ \AA.
\end{tablenotes}
\end{threeparttable}
\caption{Persistence lengths for common polymers, and biopolymers with
  filament structures.}
\label{tab:perval}
\end{center}
\end{table}

%Using  the  persistence  length  $a$  one  can  classify  biopolymers
%according to  their stiffness into rigid,  flexible, and semi-flexible
%polymers as shown in Table~\ref{tab:pers}.
%\begin{table}[H]
%\begin{center}  
%\begin{tabular}{c|c|c|c}
%\hline
%Model           & Polymer Type & $a$ to $L$ relation & Examples\\ \hline
%Rigid Rod       & Rigid          &  $a \gg L$     &  Actin, Microtubules\\
%Gaussian chain  & Flexible       &  $a \ll L$     &  \\
%Worm-like chain & Semi-flexible  &  $a \approx L$ &  High Force Extension DNA\\
%\hline
%\end{tabular}
%\label{tab:pers}
%\caption{Relation of persistence length ($a$) to contour length ($L$)
%  and polymer classification.}
%\end{center}
%\end{table}

There are other definitions of persistence length which arise when one
wants   to   take   into   account   the   electrostatic   nature   of
polyelectrolytes, for example; Skolnick and Fixman \cite{skolnick1977}
propose  and  electrostatic  persistence  length  as a  result  of  an
extension  of the  so-called  Porod-Kratky chain  to include  charges.
Another  approach is  that of  Manning, which  proposes an  ideal case
where  the charge  of the  polyelectrolyte (DNA)  would  be completely
neutralized\footnote{Manning defines DNA* as the null charge isomer of
  charged DNA.}  and for  such neutralized molecule a null persistence
length  is  defined  \cite{manning2006}.   Yet another  definition  of
persistence length by Trifonov et al. \cite{trifonov1987} appears when
``static''  and  ``dynamic''   components  are  considered.   In  such
definition the ``static'' components come from static bends like those
produced by phased A-tracts in DNA.

\section{Freely Jointed Chain (FJC)}
The end-to-end  vector $\mathbf{r}$ is  the vector which  connects the
ends of a polymer  chain and can be defined as the  sum of the vectors
connecting the monomeric units  in the chain. These connecting vectors
can be  either ``real-bond''  vectors or ``virtual-bond''  vectors and
are denoted  by $\mathbf{l}$.  The magnitude of  the end-to-end vector
is usually the quantity of interest.
\begin{gather}
\mathbf{r} = \sum_{i=1}^{n} \mathbf{l}_{i}\\
\label{eq:end2end}
r = \sqrt{\mathbf{r} \cdot \mathbf{r}}
  = \sqrt{\sum_{i,j}\mathbf{l}_{i} \cdot \mathbf{l}_{j}}
\end{gather}
Equation \ref{eq:end2end}, can also be written as:
\begin{gather}
r^2 = \sum_{i}l_{i}^{2} + 2 \sum_{i\neq j} \mathbf{l}_{i} \cdot \mathbf{l}_{j}
\end{gather}  
To  describe a  polymer  it's  necessary to  think  about the  various
conformations it  can adopt due  to its flexibility, therefore,  it is
important  to think  of polymer  related  quantities in  terms of  the
average properties  of their conformations. For  the end-to-end vector
the average of an ensemble is denoted as $<r>$, and the average of its
squared  value,  also  called  the  second moment  of  the  end-to-end
distribution, is denoted by $<r^2>$:
\begin{gather}
\label{eq:secmom}  
<r^2>=\sum_{i}<l_{i}^2> + 2\sum_{i<j}<l_{i} \cdot l_{j}>
\end{gather}  
When there is no correlation between succesive bonds we can write:
\begin{gather}
\label{eq:nocorr}
<l_{i} \cdot l_{j}> = 0
\end{gather}
The geometrical interpretation  of this is that every  bond is allowed
to  rotate  freely around  its  immediate  neighbors.   What is  meant
precisely by ``freely'',  is that bond angles can  randomly assume any
value between 0  and 360 degrees, there are  no bond-angle constraints
whatsoever.   When the number  of conformations  tend to  infinity the
average cosine of bond  angles will be zero.  Equation \ref{eq:secmom}
then keeps only the bond auto-correlation term:
\begin{gather}
<r^2> = \sum_{i=1}^{n}<l_{i}^2> = nl^2
\end{gather}  
This equation is used to describe a so-called freely-jointed chain (FJC). 

\section{Porod-Kratky or Worm Like Chain (WLC)}
If a polymer is modelled as a linear (not branched) continous and
homogenous chain its curvature at an arclength $s$ is given by the
tangential unit vector $\hat{t}$:
\begin{gather}
\hat{t}(s)=\frac{\partial{\textbf{r}(s)}}{\partial{s}}
\end{gather}
Where $\textbf{r}(s)$ is the position vector of a point in the chain
centered in the coordinate origin.
The end-to-end vector is then defined as the integral sum of the chain
curvature over the contour length of the chain as:
\begin{gather}
\textbf{r}=\int_{0}^{L}\hat{t}(s)ds
\end{gather}
The average sum of the squared end-to-end distance is then:
\begin{eqnarray}
\label{eq:wlc}
<\textbf{r}^2> & = & <\textbf{r} \cdot \textbf{r}> \nonumber \\
               & = & <\int_{0}^{L}\hat{t}(s)ds \cdot \int_{0}^{L}\hat{t}(s')ds' >\nonumber \\
               & = & \int_{0}^{L} ds \int_{0}^{L}<\hat{t}(s) \cdot \hat{t}(s')>ds' \nonumber \\
               & = & \int_{0}^{L} ds \int_{0}^{L} <\cos{\theta}_{ss'}>~ ds' \nonumber \\
               & = & \int_{0}^{L} ds \int_{0}^{L} \exp^{-\frac{|s-s'|}{a}} ds' \nonumber \\
               & = & 2aL \{ 1 - \frac{a}{L}(1-\exp^{-\frac{L}{a}})\}
\end{eqnarray}
Where  for   a  chain  of  infinite   length  $<\cos{\theta_{ss'}}>  =
\exp^{-\frac{|s-s'|}{a}}$, with $a$ being the persistence length.  The
last   equation  in   \ref{eq:wlc}   is  used   to   describe  a   so-called
worm-like-chain (WLC).

\section{Olson - Realistic}

The Hamiltonian for a \cite{czapla2009}






"length at which the orientation of the sequential bonds which make up
a polymer chain, stop being correlated.  That is, if you have just two
bonds, or a  few, they will be correlated, which is  the case in small
molecules,  but, in  polymers, you  have  a long  chain of  sequential
bonds. At some length, bonds  will become uncorrelated, but up to that
length  they were  correlated, this  is what  is meant  by persistence
length,  and,  in this  context  it's  obvious  that is  an  exclusive
property of polymers." My understanding so far.





%\section{Suggested Reads}
%From Equilibrium Statistics of Plischke and Bergersen they suggest to
%read:
%Des Cloiseaoux and Janik ()
%Rubinstein and Colby (Polymer Physics)
\bibliography{biblio}
